---
output:
  word_document: 
    reference_docx: Template_KORA.docx
    
editor_options: 
  chunk_output_type: console
  
params:
  effective.TN: NULL
  potentially.TN: NULL
  Title: NULL
  Language: NULL
  Authors: NULL
  KORAphoto: NULL
  Lynxmaster: NULL
  PhotoPredator: NULL
  LynxObs: NULL
  Compartment: NULL
  Refarea: NULL
  favorable: NULL
  Period.selected: NULL
  JuvasMother: NULL
  Species.other: NULL
  which.best.model.selected: NULL
  External.Model: NULL
---


```{r Manual Data Information, echo=FALSE}

# ------ !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!! ------ #
#     All the information which is not automatically computed, should be added here.           #     
#               This is done with the function KORAtool::KORAMonitoringBericht                 #
# ------ !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!! ------ #

  #Trap night calendar information:

  effective.TN = params$effective.TN 
  potentially.TN= params$potentially.TN 
  #Title:
  Title= params$Title 
  Language= params$Language 
  #Authors: ex."Luc Le Grand, Florin Kunz, Fridolin Zimmermann"
  Authors= params$Authors
  #KORAphoto data csv name:
  KORAphoto= params$KORAphoto
  #Lynx master data csv name:
  Lynxmaster= params$Lynxmaster
  #Photo Predator csv name:
  PhotoPredator= params$PhotoPredator
  #Lynx Observation CSV name:
  LynxObs=params$LynxObs
  #Compartment: 
  #1:"Nordostschweiz"
  #2:"Misox (Mesolcina)"
  #3:"Tessin"
  #4:"Surselva"
  #5:"Zentralschweiz Ost"
  #6:"Rhone-Nord"
  #7:"Unterwallisüd"
  #8:"Simme-Saane"
  #9:"Engadin"
  #10:"Jura Nord"
  #11:"Jura Süd"
  #12:"Mittelbünden"
  #13:"Zentralschweiz West"
  #14:"Zentralschweiz Mitte"
  #15:"Berner Oberland Ost"
  #16:"Oberwallis")
  Compartment= params$Compartment
  #Sutdy Area (Reference Area):
  # 1: "Western central Switzerland"
  # 2: "North-eastern Switzerland"  
  # 3: "North-western Alps"
  # 4: "Mid-central Switzerland"
  # 5: "Southern Jura"
  # 6: "Central Jura"
  # 7: "Northern Jura" 
  # 8: "Northern Valais"  
  Refarea = params$Refarea
  #Suitable habitat (km2):
  favorable= params$favorable
  #Period length selected (3 other 5 days)
  Period.selected= params$Period.selected
  #JuvasMother
  JuvasMother= params$JuvasMother
  #Species.other to be ploted at the end of the report
  Species.other = params$Species.other
  # Which best Model (1 to 8 or 9 if ext.model provided)
  which.best.model.selected = params$which.best.model.selected
  #External Model results to be used in the report
  External.Model= params$External.Model

```

```{r R Packages, include=FALSE}
devtools::install_github("CrocutaLupus/KORAtool")
library(KORAtool)


library(data.table)
library(knitr)#tables
library(pander)
library(flextable)



# ------ Projection : ####
#Projection to be used for the map (CH1903 / LV03):
#Warnings OK
suppressWarnings(CRS<- sp::CRS("+init=epsg:21781"))


```

```{r Import data, include=FALSE}

##### Import all the raw data needed ####

#KORA photo data:
Data<-data.table::fread(KORAphoto)
Data$TIME<-as.POSIXct(paste(Data$exposure_date,Data$exposure_time ,sep=" "), format= '%Y-%m-%d %H:%M:%S')

#Lynx master data table:
L.master<-data.table::fread(Lynxmaster)
L.master$mother<-as.character(L.master$mother)
L.master$yearOfBirth<-as.numeric(L.master$yearOfBirth)

#Text table for thanking part and method's foot note:
Text.table<-read.csv("Det_Mon_Report_Data_per_Reference_Area.csv")


##### Add sex and Juv info to Data: ####

#Select Juveniles's year of birth (previous year):
juv.year<-data.table::year(max(Data$TIME))-1

# Add info from Master Lynx Table: (L.master)

for(i in 1:length(L.master$name)){
  
  Data[Data$id_individual==L.master[i,name],"Sex"]<-L.master[i,sex]
  Data[Data$id_individual==L.master[i,name],"Juv"]<-L.master[i,yearOfBirth]
  
}

Data$Juv<-as.character(Data$Juv)

for(i in 1:nrow(Data)){
    if(Data[i ,Juv]==juv.year & !is.na(Data[i ,Juv])){
    Data[i ,"Juv"]<-"Juv"
  }
}

Data[Data$Sex=="","Sex"]<-NA
Data[Data$Juv!="Juv","Juv"]<-NA

```

```{r Table sites information, echo=FALSE}
#Table all sites:
Table.Sites<-data.table::data.table(SiteName=sort(unique(Data[,site_name])),
                                    Npictures=0,
                                    Npicutreslynx=0)


for(i in 1:length(Table.Sites$SiteName)){
  
  Table.Sites[i,"Npictures"]<-length(Data[Data$site_name==Table.Sites[i,SiteName],file_name])
  Table.Sites[i,"Npicutreslynx"]<-length(Data[Data$site_name==Table.Sites[i,SiteName] &
                                                Data$animal_species=="Lynx lynx",file_name])
}

     
Table.Sites$RunningNumber<-1:length(Table.Sites$SiteName)

Table.Sites<-flextable(Table.Sites)
Table.Sites <- set_caption(Table.Sites, caption = " Summary Sites Session. Please control in KORA photo that each site has at least one picture of something.")
Table.Sites<-font(Table.Sites,fontname = "Calibri", part = "all")
Table.Sites<-fontsize(Table.Sites,size = 12, part = "body")
Table.Sites<- autofit(Table.Sites) 
Table.Sites<-height_all(Table.Sites, height = .26)
Table.Sites<- hrule(Table.Sites, rule = "exact")

```

```{r Main Map, echo = FALSE}

#Note: Individual considered as Juv are not plotted

KORAtool::KORAmapsex(KORA.Photo.Output=Data,
  species="Lynx lynx",
  Buffer.map=0.03,
  Zoom.map=10,
  IDremove="U",
  Start= min(Data$TIME), #For the main map, we want all the lynx data plotted
  Stop=max(Data$TIME), #For the main map, we want all the lynx data plotted
  Pattern="T",#pattern not resent but used not to block the function
  Buffer.label=2000,
  Name.Map="Map_Report",
  Refarea=Refarea,
  Red.point.ID="U")
```

```{r 60 days subset, echo=FALSE}

Start<-as.POSIXct(paste(Data[1,session_study_start_date],
                          Data[1,session_study_start_time],sep=" "),
                    format= '%Y-%m-%d %H:%M:%S')
  
Stop<-as.POSIXct(paste(Data[1,session_study_end_date],
                         Data[1,session_study_end_time],sep=" "),
                   format= '%Y-%m-%d %H:%M:%S')

#Is there any lynx that was seen before or after the 60 days? 
Seen.external<-Data[,id_individual][which(!(unique(Data[Data$animal_species== "Lynx lynx",id_individual]) %in%
unique(Data[Data$TIME>Start & Data$TIME<Stop & Data$animal_species== "Lynx lynx",id_individual])))]

#Subset Data so that only information during the 60 days is used
DataFULL<-Data
Data<-Data[Data$TIME>Start & Data$TIME< Stop,]

```

```{r abstract number automatic 1st part, echo=FALSE}


#Number of unique sites (based on coordinates (uses all data also before/after 60 days)
Sites<-length(unique(paste(DataFULL$x,DataFULL$y,sep="")))

#Count Lynx
Lynx.Table<-data.table::data.table(ID=unique(Data[Data$animal_species=="Lynx lynx" &
                                   Data$id_individual!="U",id_individual]))


for(i in 1:length(Lynx.Table$ID)){
  Lynx.Table[i,"YOB"]<-L.master[L.master$name==Lynx.Table$ID[i],yearOfBirth]
  Lynx.Table[i,"Sex"]<-L.master[L.master$name==Lynx.Table$ID[i],sex]
  Lynx.Table[i,"mother"]<-L.master[L.master$name==Lynx.Table$ID[i],mother]
  Lynx.Table[i,"Flank"]<-L.master[L.master$name==Lynx.Table$ID[i],chipNo]
}
Lynx.Table$Flank<-as.character(Lynx.Table$Flank)
Lynx.Table[!is.na(Lynx.Table$Flank),"Flank"]<-"B"
Lynx.Table[grepl("B",Lynx.Table$ID) & is.na(Lynx.Table$Flank),"Flank"]<-"B"
Lynx.Table[grepl("R",Lynx.Table$ID) & is.na(Lynx.Table$Flank),"Flank"]<-"R"
Lynx.Table[grepl("L",Lynx.Table$ID) & is.na(Lynx.Table$Flank),"Flank"]<-"L"

#Table with only adults
Lynx.Table.Adult<-Lynx.Table[Lynx.Table$YOB!=juv.year | is.na(Lynx.Table$YOB),]

#Count minimum adults
N.ind.lynx<-length(Lynx.Table.Adult[Lynx.Table.Adult$Flank=="B",ID])+
            max(length(Lynx.Table.Adult[Lynx.Table.Adult$Flank=="L",ID]),
                length(Lynx.Table.Adult[Lynx.Table.Adult$Flank=="R",ID]))

N.juv<-length(Lynx.Table[Lynx.Table$YOB==juv.year & Lynx.Table$Flank=="B",ID])+
            max(length(Lynx.Table[Lynx.Table$YOB==juv.year & Lynx.Table$Flank=="R",ID]),
                length(Lynx.Table[Lynx.Table$YOB==juv.year & Lynx.Table$Flank=="L",ID]))



#Event:

## create column with ID of captured Individual, juvenile catches count as catch of the mother
Data$ID.mummy<-Data$id_individual

for(i in 1:length(Lynx.Table[Lynx.Table$YOB==juv.year,ID])){
  if(Lynx.Table[Lynx.Table$ID==Lynx.Table[Lynx.Table$YOB==juv.year,ID][i],mother]!=""){
    Data[Data$id_individual==Lynx.Table[Lynx.Table$YOB==juv.year,ID][i],"ID.mummy"]<-Lynx.Table[Lynx.Table$ID==Lynx.Table[Lynx.Table$YOB==juv.year,ID][i],mother]
  } #mother not known
}


#Select if Juveniles are counted as mother or not
if(JuvasMother==TRUE){
  Data$ID<-Data$ID.mummy
}
if(JuvasMother==FALSE){
  Data$ID<-Data$id_individual
}

# Create Event Table
Event<-KORAtool::EvCountR(Table_Object=Data[!grepl(paste("U",paste(Lynx.Table[Lynx.Table$YOB==juv.year,ID],collapse="|"),sep="|"),
                                         Data$ID) & Data$animal_species=="Lynx lynx",],Event_length=30)



```

```{r Lynx Table, echo=FALSE}

Event.report<-Event

Event.report<-merge(x = Event.report, y = Lynx.Table, by="ID", all.x = TRUE)
Event.report$Flank<-NULL
Event.report$YOB<-as.character(Event.report$YOB)

Event.report[Event.report$Sex=="unknown","Sex"]<-NA
Event.report[Event.report$Sex=="male","Sex"]<-"M"
Event.report[Event.report$Sex=="female","Sex"]<-"F"

# --- Add first seen

#Import Raw Data (CSV from KORA Data): 
  LynxMaster.table<-suppressWarnings(data.table::fread(Lynxmaster))
  LynxObs.table<-data.table::fread(LynxObs,select=c("lynx_ID","image_uid","date","x","y"))
  PhotoPredator.table<-data.table::fread(PhotoPredator,select=c("id_individual","exposure_date","session_name","x","y"))
#Select interesting Columns:  
  First.seen.table<-LynxMaster.table[,c("name","coatPattern","yearOfBirth","deathDate","mother")]

#Fill in info First/Last seen: 
 for(i in 1:length(First.seen.table$name)){
   First.seen.table[i,"FirstSeen"]<-suppressWarnings(min(min(as.POSIXct(LynxObs.table[LynxObs.table$lynx_ID==as.character(First.seen.table[i,name]),date],format='%Y-%m-%d',tz="")),
                                   min(as.POSIXct(PhotoPredator.table[PhotoPredator.table$id_individual==as.character(First.seen.table[i,name]),exposure_date],format='%Y-%m-%d'))))
   First.seen.table[i,"LastSeen"]<- suppressWarnings(max(max(as.POSIXct(LynxObs.table[LynxObs.table$lynx_ID==as.character(First.seen.table[i,name]),date],format='%Y-%m-%d',tz="")),
                                   max(as.POSIXct(PhotoPredator.table[PhotoPredator.table$id_individual==as.character(First.seen.table[i,name]),exposure_date],format='%Y-%m-%d'))))
}

Event.report<-merge(Event.report, First.seen.table[,c("name","FirstSeen")],all.x = TRUE,by.x = "ID",by.y = "name")

#Check if some lynx were discovered during the session:

for(i in 1:nrow(Event.report)){
  Event.report[i,"FirstTimeSeen"]<-Event.report[i,FirstSeen]>Start
}

New.lynx<-Event.report[Event.report$FirstTimeSeen==TRUE,ID]

Event.report$FirstTimeSeen<-NULL

#First seen only show year in final table
Event.report$FirstSeen<-as.character(year(Event.report$FirstSeen))

# --- Add juveniles info to each known mother
for(i in 1:length(unique(Lynx.Table[Lynx.Table$YOB==juv.year,mother]))){
  Event.report[Event.report$ID==unique(Lynx.Table[Lynx.Table$YOB==juv.year,mother])[i],"Juv"]<-paste(
    Lynx.Table[Lynx.Table$mother==unique(Lynx.Table[Lynx.Table$YOB==juv.year,mother])[i] & !is.na(Lynx.Table$mother),ID],collapse=", ")
}


#Add canton seen:
for(i in 1:length(Event.report$ID)){
  
  if(JuvasMother==TRUE){
   Event.report[i,"Canton"]<-paste(unique(Data[Data$ID.mummy==Event.report[i,ID],loc_canton]),collapse = ", ")
  }  
    
   if(JuvasMother==FALSE){
   Event.report[i,"Canton"]<-paste(unique(Data[Data$id_individual==Event.report[i,ID],loc_canton]),collapse = ", ")
  }  
  
}


#Rename Table
Event.report<-Event.report[,c("ID","Event","N pictures","N site","YOB","FirstSeen","Sex","mother","Juv","Canton")]


#Remove some columns (discussion with Florin and Fridolin 2021-09-01)
Event.report<-Event.report[,-c("N pictures","N site","YOB")]

if(Language=="FR"){names(Event.report)<-c("ID","Événement(s)","Connu depuis","Sexe","Mère","Juvénile(s)","Canton(s)")}
if(Language=="DE"){names(Event.report)<-c("ID","Ereignisse","Bekannt seit","Geschlecht","Mutter","Juvenil(e)","Kanton(e)")}


#Total as last:
bindtotal<-Event.report[Event.report$ID=="Total",]
Event.report<-Event.report[Event.report$ID!="Total",]
Event.report<-rbind(Event.report,bindtotal)

#New lynx in bold (get line number for later)
New.lynx<-Event.report[,which(Event.report$ID %in% New.lynx)]

# Data table into flextable to plot:

Event.report<-flextable(Event.report)

if(Language=="FR"){
 Event.report <- set_caption(Event.report, caption = "Lynx détectés dans l’aire de référence pendant les 60 nuits d’échantillonnage. Un événement comprend toutes les images  à un site donné séparées de moins de 30 minutes. Connu depuis\ : année de la première observation. Mère\ : mère des lynx indépendants quand elle est connue. Juvénile(s)\ : juvéniles des lynx femelles indépendantes quand elles connues. Canton(s)\ : cantons dans lesquels les lynx ont été observés lors de la session. Les lynx qui ont été détecté pour la première fois lors de la session sont mis en évidence en gras.",autonum = officer::run_autonum(
  seq_id = "table",
  pre_label = "Tab. ",
  post_label = ". ",
  bkm = NULL,
  bkm_all = FALSE,
  prop = officer::fp_text(bold= TRUE, font.size = 10, font.family= "Calibri") ,
  start_at = ""
)) 
}

if(Language=="DE"){
 Event.report <- set_caption(Event.report, caption = "Luchse, die in den 60 Nächten des Durchgangs Fotografierte wurden. Ein Ereignis umfasst alle Bilder an einem bestimmten Ort, die weniger als 30 Minuten auseinander liegen. Bekannt seit: Jahr der ersten Beobachtung. Mutter: Mutter von unabhängigen Luchsinen, wenn bekannt. Juvenil(e): Jungtiere von unabhängigen Luchsen, sofern bekannt. Kanton(e): Kantone, in denen während der Session Luchse beobachtet wurden. Luchse, die während der Session zum ersten Mal entdeckt wurden, sind fett hervorgehoben.",autonum = officer::run_autonum(
  seq_id = "table",
  pre_label = "Tab. ",
  post_label = ". ",
  bkm = NULL,
  bkm_all = FALSE,
  prop = officer::fp_text(bold= TRUE, font.size = 10, font.family= "Calibri") ,
  start_at = ""
)) 
}

# --- Add footnote:

#Texte juvéniles sans mère:

if(Language== "FR"){
 txt.juv<-"Juvénile(s) sans mère connue\ : "

if(length(Lynx.Table[Lynx.Table$YOB==juv.year & Lynx.Table$mother=="",ID])>0){
 for(i in 1:length(Lynx.Table[Lynx.Table$YOB==juv.year & Lynx.Table$mother=="",ID])){
  
 txt.juv<- paste(txt.juv,
    Lynx.Table[Lynx.Table$YOB==juv.year & Lynx.Table$mother=="",ID][i]," (Nb photo = ",
      length(Data[Data$id_individual==Lynx.Table[Lynx.Table$YOB==juv.year & Lynx.Table$mother=="",ID][i],file_name]),
    ") ",sep="")

  } 
}else{
  
txt.juv<-"Tous les juvéniles photographiés ont pu être associé à leur mère."

} 
}

if(Language== "DE"){
 txt.juv<-"Jungtiere ohne bekannte Mutter: "

if(length(Lynx.Table[Lynx.Table$YOB==juv.year & Lynx.Table$mother=="",ID])>0){
 for(i in 1:length(Lynx.Table[Lynx.Table$YOB==juv.year & Lynx.Table$mother=="",ID])){
  
 txt.juv<- paste(txt.juv,
    Lynx.Table[Lynx.Table$YOB==juv.year & Lynx.Table$mother=="",ID][i]," (N Bilder = ",
      length(Data[Data$id_individual==Lynx.Table[Lynx.Table$YOB==juv.year & Lynx.Table$mother=="",ID][i],file_name]),
    ") ",sep="")

  } 
}else{
  
txt.juv<-"Alle fotografierten Jungtiere konnten mit ihren Müttern in Verbindung gebracht werden."

} 
}

#Text JuvasMother:

if(Language=="FR"){
 if(JuvasMother==TRUE){
  
txt.juvasmother<-"A cause de leur fort taux de disparition (mortalité et dispersion) les individus juvéniles photographiés au cours du monitoring sont identifiés et considérés comme une capture de leur mère. Si la mère est connue, leurs noms figurent dans la colonne juvénile(s)." 
  
}else{
  
txt.juvasmother<-"A cause de leur fort taux de disparition (mortalité et dispersion) les individus juvéniles photographiés au cours du monitoring sont identifiés, mais pas considérés. Si la mère est connue, leurs noms figurent dans la colonne juvénile(s)."

} 
}

if(Language=="DE"){
 if(JuvasMother==TRUE){
  
txt.juvasmother<-"Aufgrund ihrer hohen Verschwindungsrate (Sterblichkeit und Ausbreitung) werden Jungtiere, die während der Überwachung fotografiert werden, identifiziert und als Fang ihrer Mutter betrachtet. Wenn die Mutter bekannt ist, erscheinen die Namen in der Spalte Jugendliche." 
  
}else{
  
txt.juvasmother<-"Aufgrund ihrer hohen Verschwindungsrate (Sterblichkeit und Ausbreitung) werden Jungtiere, die während der Überwachung fotografiert wurden, zwar identifiziert, aber nicht berücksichtigt. Wenn die Mutter bekannt ist, erscheinen die Namen in der Spalte Jugendliche."

} 
}


#Create footnote:
Event.report<- footnote( Event.report, i = 1,j=c(1,2),
            value = as_paragraph(
                      c(txt.juv,
                        txt.juvasmother)),
            ref_symbols = c("1","2"),
            part = "header")

Event.report <- bold(Event.report, bold = TRUE, part = "footer")

#New lynx in bold (get line number for later)
Event.report <- bold(Event.report, bold = TRUE, part = "body",i=New.lynx)

Event.report<-font(Event.report,fontname = "Calibri", part = "all")
Event.report<-fontsize(Event.report,size = 12, part = "body")

Event.report<- autofit(Event.report) 
Event.report<-height_all(Event.report, height = .26)
Event.report<- hrule(Event.report, rule = "exact")

```

```{r Opp Mon Map, echo=FALSE}

# KORAmapopp using LynxObs (Opp. mon observations)

Plot.Opp.Mon<-KORAtool::KORAmapopp(LynxObs= LynxObs,
                              Start=Start,
                              Stop=Stop,
                              Compartment=Compartment,
                              Refarea=Refarea,
                              IDremove=c("U","lx","XXXX"),
                              Buffer.polygon=2000)

ggplot2::ggsave("Plot_Opp_Mon.jpeg",plot=Plot.Opp.Mon,
                    units = "cm",
                    width = 16.5,
                    height = 20)



# -- Plot function Monitoring Opp

Plot_KORA_Report<-function(Species){
  #Import shapefile compartment
Komp <- sf::read_sf(dsn = "MAP_Data/Luchs_Komp_21_07_2015_new.shp")
  
# -- Study Area #
study_area<-sp::bbox(as.matrix(Komp$geometry[Compartment][[1]]))
study_area.origin<-sp::bbox(as.matrix(Komp$geometry[Compartment][[1]]))
#Add x% around the BBox to have some extra map area
  
  study_area[1,1]<-study_area[1,1]-round(study_area[1,1]*0.02) #x min
  study_area[2,1]<-study_area[2,1]-round(study_area[2,1]*6*0.02) #y min
  study_area[1,2]<-study_area[1,2]+round(study_area[1,2]*0.02) #x max
  study_area[2,2]<-study_area[2,2]+round(study_area[2,2]*0.02) #y max
  
study_area<-rgeos::readWKT(paste("POLYGON((",
                                   study_area[1,1]," ",study_area[2,1],",",
                                   study_area[1,1]," ",study_area[2,2],",",
                                   study_area[1,2]," ",study_area[2,2],",",
                                   study_area[1,2]," ",study_area[2,1],",",
                                   study_area[1,1]," ",study_area[2,1],"))",sep=""),p4s= CRS)

  

# --- Import shapefile Study area Polygon
suppressWarnings(Rcompartment <- raster::shapefile("MAP_Data/Reference_areas_alln.shp"))
Rcompartment<-Rcompartment[Refarea,]

#Import shapefile compartment
suppressWarnings(Komp <- raster::shapefile("MAP_Data/Luchs_Komp_21_07_2015_new.shp"))
Komp<-Komp[Compartment,]

# ------ Open Source Map
  
#study area BBox in lat long
study_area_lat_long <- sp::spTransform(study_area, sp::CRS("+init=epsg:4326"))
  
  LAT1 = study_area_lat_long@bbox[2,1] ; LAT2 = study_area_lat_long@bbox[2,2]
  LON1 = study_area_lat_long@bbox[1,1] ; LON2 = study_area_lat_long@bbox[1,2]
  
#Get the map
#warnings OK
suppressWarnings(map <- OpenStreetMap::openmap(c(LAT2,LON1), c(LAT1,LON2), zoom = NULL, #can be replaced by NULL
                                                 type = c("stamen-terrain")[1],
                                                 mergeTiles = TRUE))
  
#Correct projection
#warnings OK
suppressWarnings(map <- OpenStreetMap::openproj(map, projection = "+init=epsg:21781"))
  
# ------ Build map 

# --- Open Source Map in ggplot:
map<-OpenStreetMap::autoplot.OpenStreetMap(map)+
ggplot2::theme(axis.title=ggplot2::element_blank(),
                   axis.text=ggplot2::element_blank(),
                   axis.ticks=ggplot2::element_blank(),
                   panel.border = ggplot2::element_rect(colour = "white", fill=NA, size=25))


# --- Add Scale:
  
  # distance on x axes:
  dist.scale<-plyr::round_any(round(((study_area@bbox[1,2]-study_area@bbox[1,1])/1000)/4), 10, f = ceiling)
  
  # scale thickness:
  s.thick<-(0.01*(study_area@bbox[2,2]-study_area@bbox[2,1]))
  
  # scale black rectangle
  xleft<-study_area@bbox[1,1]+((study_area.origin[1,1]-study_area@bbox[1,1])/3)#left
  xright<-xleft+dist.scale*1000#right
  ybottom<-study_area.origin[2,1]-4*s.thick#bottom
  ytop<-study_area.origin[2,1]-3*s.thick#top

  map<-map+
    ggplot2::geom_rect(mapping=ggplot2::aes(xmin=xleft, xmax=xright, ymin=ybottom, ymax=ytop),
                       fill=c("black"),
                       inherit.aes = FALSE)+
    ggplot2::geom_text(x=xright+(2/5)*dist.scale*1000, y=ytop, label=paste(dist.scale,"Km",sep=" "), cex=6, color ="black")

  
# --- Add other layers:

map<-map+
#KOMP
ggplot2::geom_polygon(data = Komp@polygons[[1]], ggplot2::aes(x=long, y=lat,group = group),
                               colour="black", fill="white", alpha=0.4, lwd=1.1)+
#Refarea
ggplot2::geom_polygon(data = Rcompartment@polygons[[1]], ggplot2::aes(x=long, y=lat),
                               colour="darkblue", fill=NA, alpha=1, lwd=1.1)+
#Points Sites
ggplot2::geom_point(data=DataFULL,ggplot2::aes(x,y), col="white", pch=19,cex=6)+
      ggplot2::geom_point(data=DataFULL,ggplot2::aes(x,y),col="black", pch=1,cex=6)+
#Points Sites positive for species
ggplot2::geom_point(data=DataFULL[DataFULL$animal_species==Species,],ggplot2::aes(x,y), col="black", pch=19,cex=3)

  
print(map)
  
}

```

```{r Occasion Tables, echo=FALSE}
# Create table occasion:
Occ.table<-data.table(ID=unique(Lynx.Table.Adult$ID))


# To carry the analyses of the lynx monitoring, we test periods of 3 days and periods of 5 days

for(Period in c(3,5)){
  
# ---- Create Empty Occurrence Matrix  
occasions<-seq(from = Start,to = Stop, by = paste(Period,"days", sep=" "))
Occ.table<-data.table::data.table(ID = unique(Lynx.Table.Adult$ID))
if(Period==3){
  Occ.table[,c(as.character(occasions[-21])):= 0]
}
if(Period==5){
  Occ.table[,c(as.character(occasions[-13])):= 0]
}

# ---- Fill in Matrix 

#observation of juvenile counts as an observation of the mother

if(JuvasMother==TRUE){
  for(i in 1:length(Occ.table$ID)){
  for(j in 2:ncol(Occ.table)){
    Data_loop<- Data[Data$TIME > as.POSIXct(names(Occ.table)[j])  &
                         Data$TIME < as.POSIXct(names(Occ.table)[j]) + Period*86400 & #select days occasion
                         Data$ID.mummy == Occ.table[i,ID],c("TIME","file_name")]
    if(length(Data_loop$file_name)!=0){
      Occ.table[i,j]<-1
    }else{Occ.table[i,j]<-0}
  }
}
}

#observation of juvenile does not count as an observation of the mother

if(JuvasMother==FALSE){
  for(i in 1:length(Occ.table$ID)){
  for(j in 2:ncol(Occ.table)){
    Data_loop<- Data[Data$TIME > as.POSIXct(names(Occ.table)[j])  &
                         Data$TIME < as.POSIXct(names(Occ.table)[j]) + Period*86400 & #select days occasion
                         Data$id_individual == Occ.table[i,ID],c("TIME","file_name")]
    if(length(Data_loop$file_name)!=0){
      Occ.table[i,j]<-1
    }else{Occ.table[i,j]<-0}
  }
}
}


# ---- Check if an individual has no single catch within the study period (60nights)
for(i in 1:length(Occ.table$ID)){
  if(sum(Occ.table[1,2:ncol(Occ.table)])==0){
    warning("warning: ID has not been seen during the 60 days.")
  }
}


# ---- Occ.table for Plot cumulative (2 table, one per period length)

if(Period==3){
Occ.table.3<-Occ.table
Occ.table.plot.3<-dcast(melt(Occ.table, id.vars = "ID"), variable ~ ID)
names(Occ.table.plot.3)[1]<-"TIME"
#number of captures per occasion
Occ.table.plot.3$SUM.occasion<-rowSums(Occ.table.plot.3[,-1])
#cumulative number of captures per occasion
Occ.table.plot.3$SUM.occasion.cumulative<-cumsum(Occ.table.plot.3$SUM.occasion)

#Cumulative number of ID lynx

Occ.table.plot.3$SUM.ID.cumulative<-sum(Occ.table.plot.3[1,2:(length(Occ.table.plot.3)-2)])
Sum.ID<-as.numeric(Occ.table.plot.3[1,2:(length(Occ.table.plot.3)-3)])

for(i in 2:20){
 Sum.ID<-Sum.ID+as.numeric(Occ.table.plot.3[i,2:(length(Occ.table.plot.3)-3)])

 Sum.ID<-replace(Sum.ID, Sum.ID==2, 1)
 
 Occ.table.plot.3[i,"SUM.ID.cumulative"]<-sum(Sum.ID)
  
}

}

if(Period==5){
Occ.table.5<-Occ.table
Occ.table.plot.5<-dcast(melt(Occ.table, id.vars = "ID"), variable ~ ID)
names(Occ.table.plot.5)[1]<-"TIME"
#number of captures per occasion
Occ.table.plot.5$SUM.occasion<-rowSums(Occ.table.plot.5[,-1])
#cumulative number of captures per occasion
Occ.table.plot.5$SUM.occasion.cumulative<-cumsum(Occ.table.plot.5$SUM.occasion)

#Cumulative number of ID lynx

Occ.table.plot.5$SUM.ID.cumulative<-sum(Occ.table.plot.5[1,2:(length(Occ.table.plot.5)-2)])
Sum.ID<-as.numeric(Occ.table.plot.5[1,2:(length(Occ.table.plot.5)-3)])

for(i in 2:12){
 Sum.ID<-Sum.ID+as.numeric(Occ.table.plot.5[i,2:(length(Occ.table.plot.5)-3)])

 Sum.ID<-replace(Sum.ID, Sum.ID==2, 1)
 
 Occ.table.plot.5[i,"SUM.ID.cumulative"]<-sum(Sum.ID)
  
}

}

}

```

```{r closure analyses, echo=FALSE}

# ---- Closed Test:

for(Period in c(3,5)){
  
#Create table Sites info + read trap
Lynx_trapXY<-unique(Data[,c("site_name","x","y")])
names(Lynx_trapXY)[1]<-"trapID"
traps.lynx <- secr::read.traps(data = Lynx_trapXY)

#Create table observation info
Lynx_captXY<-data.table(Session=1,
                        ID=rep(Lynx.Table.Adult$ID,each=(60/Period)*length(Lynx_trapXY$trapID)),
                        Occasion=rep(rep(1:(60/Period),each=length(Lynx_trapXY$trapID)),length(Lynx.Table.Adult$ID)),
                        X=rep(Lynx_trapXY$x),
                        X=rep(Lynx_trapXY$y),
                        TrapID=rep(Lynx_trapXY$trapID),
                        Seen="NO")

if(Period==3){
  occasions<-seq(from = Start,to = Stop, by = paste(Period,"days", sep=" "))
  occasions<-occasions[-21]
  
  #Fill in information if lynx seen during period at given site
  for(i in 1:length(Lynx_captXY$Session)){
    
  if(JuvasMother==TRUE){
    Data_loop<- Data[Data$TIME > as.POSIXct(occasions[Lynx_captXY[i,Occasion]])  &
                         Data$TIME < as.POSIXct(occasions[Lynx_captXY[i,Occasion]]) + Period*86400 & #select days occasion
                         Data$ID.mummy == Lynx_captXY[i,ID] &
                         Data$site_name== Lynx_captXY[i,TrapID],c("TIME","file_name")]
  }
  
  if(JuvasMother==FALSE){
    Data_loop<- Data[Data$TIME > as.POSIXct(occasions[Lynx_captXY[i,Occasion]])  &
                         Data$TIME < as.POSIXct(occasions[Lynx_captXY[i,Occasion]]) + Period*86400 & #select days occasion
                         Data$id_individual == Lynx_captXY[i,ID] &
                         Data$site_name== Lynx_captXY[i,TrapID],c("TIME","file_name")]
  }
  
  if(length(Data_loop$file_name)>0){
    Lynx_captXY[i,"Seen"]<-"YES"
  }
  }
  
}
if(Period==5){
  
  #Occasions starting data/time
  occasions<-seq(from = Start,to = Stop, by = paste(Period,"days", sep=" "))
  occasions<-occasions[-13]
  
  #Fill in information if lynx seen during period at given site
  for(i in 1:length(Lynx_captXY$Session)){
    
  if(JuvasMother==TRUE){
  Data_loop<- Data[Data$TIME > as.POSIXct(occasions[Lynx_captXY[i,Occasion]])  &
                         Data$TIME < as.POSIXct(occasions[Lynx_captXY[i,Occasion]]) + Period*86400 & #select days occasion
                         Data$ID.mummy == Lynx_captXY[i,ID] &
                         Data$site_name== Lynx_captXY[i,TrapID],c("TIME","file_name")]
  }
    
  if(JuvasMother==FALSE){
  Data_loop<- Data[Data$TIME > as.POSIXct(occasions[Lynx_captXY[i,Occasion]])  &
                         Data$TIME < as.POSIXct(occasions[Lynx_captXY[i,Occasion]]) + Period*86400 & #select days occasion
                         Data$id_individual == Lynx_captXY[i,ID] &
                         Data$site_name== Lynx_captXY[i,TrapID],c("TIME","file_name")]
  }  
    
    
  if(length(Data_loop$file_name)>0){
    Lynx_captXY[i,"Seen"]<-"YES"
  }
  }
  
  
}



Lynx_captXY<-Lynx_captXY[Lynx_captXY$Seen=="YES",-c("TrapID","Seen")]

# --- Closure Test

if(Period==3){
  # ---- Create capthist 
  suppressWarnings(Lynx.CHxy.3  <- secr::make.capthist (Lynx_captXY, traps.lynx, fmt = "XY"))
  #warnings OK it produces the same results as in the program
  
  # ---- Closure test
  suppressWarnings(closure.result.3<-secr::closure.test(Lynx.CHxy.3,SB=TRUE))
  #warnings if pop too small
  
  # ---- Output for Mark program
  
  #Empty table
  inp.Mark<-data.table::data.table(ID=Lynx.Table.Adult$ID,ch="empty")
  #needs data.frame
  Occ.table.plot.3.1<-as.data.frame(Occ.table.plot.3)
  for(i in 1:length(Lynx.Table.Adult$ID)){
    inp.Mark[i,"ch"]<-paste( Occ.table.plot.3.1[,inp.Mark$ID[i]] ,collapse = "")
  }
  #process (RMark format)
  inp.Mark=RMark::process.data(inp.Mark)
  #output
  RMark::export.chdata(data=inp.Mark, filename=paste(ReportName,"period_3",sep="_"), covariates = NULL, replace = TRUE)
  
}

if(Period==5){
  # ---- Create capthist  
  suppressWarnings(Lynx.CHxy.5  <- secr::make.capthist (Lynx_captXY, traps.lynx, fmt = "XY"))
  #warnings OK it produces the same results as in the program
  
  # ---- Closure test
  suppressWarnings(closure.result.5<-secr::closure.test(Lynx.CHxy.5,SB=TRUE))
  #warnings if pop too small - do it any way like in program
  
  # ---- Output for Mark program
  
  #Empty table
  inp.Mark<-data.table::data.table(ID=Lynx.Table.Adult$ID,ch="empty")
  #needs data.frame
  Occ.table.plot.5.1<-as.data.frame(Occ.table.plot.5)
  for(i in 1:length(Lynx.Table.Adult$ID)){
    inp.Mark[i,"ch"]<-paste( Occ.table.plot.5.1[,inp.Mark$ID[i]] ,collapse = "")
  }
  #process (RMark format)
  inp.Mark=RMark::process.data(inp.Mark)
  #output
  RMark::export.chdata(data=inp.Mark, filename=paste(ReportName,"period_5",sep="_"), covariates = NULL, replace = TRUE)
}

}

```

```{r SECR analyses, echo= FALSE, message=FALSE, results='hide', warning=FALSE}

# ----------------------------- !!!!!----------------------------------------- #
# It is assumed that MARK.EXE is located in directory "C:/Program Files/Mark". #
# https://cran.r-project.org/web/packages/RMark/RMark.pdf                      #
# ----------------------------- !!!!!----------------------------------------- #



#Capture History Period=3:
CaptHist.table.3<-data.table(ID=Occ.table.3$ID)
for( i in 1:length(Occ.table.3$ID)){
CaptHist.table.3[i,"ch"]<-paste(as.numeric(Occ.table.3[i,2:length(Occ.table.3)]),collapse = "")
}

#Capture History Period=5:
CaptHist.table.5<-data.table(ID=Occ.table.5$ID)
for( i in 1:length(Occ.table.5$ID)){
CaptHist.table.5[i,"ch"]<-paste(as.numeric(Occ.table.5[i,2:length(Occ.table.5)]),collapse = "")
}

#R MArk Analzses function
lynx.Mark.models=function(CaptHist.table)
{
  #
  # Define parameter models
  #
  pdotshared=list(formula=~1,share=TRUE)
  ptimeshared=list(formula=~time,share=TRUE)
  pmixture=list(formula=~mixture)
  #
  # Run assortment of models
  #
  #
  # Capture Closed models
  #
  # M0: constant p=c
  Lynx.m0=RMark::mark(CaptHist.table,model="Closed",
                    model.parameters=list(p=pdotshared))

  # Mt: Variation accross occasions. time varying p=c
  Lynx.mt=RMark::mark(CaptHist.table,model="Closed",
                    model.parameters=list(p=ptimeshared))
  # Mh: Variation among individuals
  Lynx.Mh=RMark::mark(CaptHist.table,model="HetClosed",
                     model.parameters=list(p=pmixture))
  
  # Return model table and list of models
  #
  return(RMark::collect.models() )
}


# fit models in mark by calling function created above
# warnings ok

#suppressWarnings(Lynx.Mark.results.3<-lynx.Mark.models(CaptHist.table.3))
#suppressWarnings(Lynx.Mark.results.5<-lynx.Mark.models(CaptHist.table.5))


#Select best model:
# Create Mark Table:
Mark.Table<-data.table(Period=rep(c(3,5),each=4),
                       Model=c("M0","Mb","Mt","Mh"),
                       AIC=0,
                       N=0,
                       Min=0,
                       Max=0)


# Add AICc from RMARK to MArk.Table 
#(to get same value as in Mark programm, unadjusted for Mt and Mh, ex. Lynx.Mark.results.3$Lynx.Mh$results$AICc.unadjusted)
#Mark.Table[Mark.Table$Period==3 & Mark.Table$Model=="M0","AICc"]<-round(Lynx.Mark.results.3$Lynx.m0$results$AICc,2)
#Mark.Table[Mark.Table$Period==3 & Mark.Table$Model=="Mt","AICc"]<-round(Lynx.Mark.results.3$Lynx.mt$results$AICc,2)
#Mark.Table[Mark.Table$Period==3 & Mark.Table$Model=="Mh","AICc"]<-round(Lynx.Mark.results.3$Lynx.Mh$results$AICc,2)

#Mark.Table[Mark.Table$Period==5 & Mark.Table$Model=="M0","AICc"]<-round(Lynx.Mark.results.5$Lynx.m0$results$AICc,2)
#Mark.Table[Mark.Table$Period==5 & Mark.Table$Model=="Mt","AICc"]<-round(Lynx.Mark.results.5$Lynx.mt$results$AICc,2)
#Mark.Table[Mark.Table$Period==5 & Mark.Table$Model=="Mh","AICc"]<-round(Lynx.Mark.results.5$Lynx.Mh$results$AICc,2)

# Estimation N lynx
closedN.3<-secr::closedN(Lynx.CHxy.3, estimator = c("null","zippin","darroch","betabinomial"),
                       level = 0.95, maxN = 1e+07, dmax = 10 )

closedN.5<-secr::closedN(Lynx.CHxy.5, estimator = c("null","zippin","darroch","betabinomial"),
                       level = 0.95, maxN = 1e+07, dmax = 10 )



# Add info in Mark.Table Period = 3
Mark.Table[Mark.Table$Period==3 & Mark.Table$Model=="M0","AIC"]<-round(closedN.3$AIC[1],2)
Mark.Table[Mark.Table$Period==3 & Mark.Table$Model=="Mb","AIC"]<-round(closedN.3$AIC[2],2)
Mark.Table[Mark.Table$Period==3 & Mark.Table$Model=="Mt","AIC"]<-round(closedN.3$AIC[3],2)
Mark.Table[Mark.Table$Period==3 & Mark.Table$Model=="Mh","AIC"]<-round(closedN.3$AIC[4],2)

Mark.Table[Mark.Table$Period==3 & Mark.Table$Model=="M0","N"]<-round(closedN.3$Nhat[1],0)
Mark.Table[Mark.Table$Period==3 & Mark.Table$Model=="Mb","N"]<-round(closedN.3$Nhat[2],0)
Mark.Table[Mark.Table$Period==3 & Mark.Table$Model=="Mt","N"]<-round(closedN.3$Nhat[3],0)
Mark.Table[Mark.Table$Period==3 & Mark.Table$Model=="Mh","N"]<-round(closedN.3$Nhat[4],0)

Mark.Table[Mark.Table$Period==3 & Mark.Table$Model=="M0","SE"]<-round(closedN.3$seNhat[1],2)
Mark.Table[Mark.Table$Period==3 & Mark.Table$Model=="Mb","SE"]<-round(closedN.3$seNhat[2],2)
Mark.Table[Mark.Table$Period==3 & Mark.Table$Model=="Mt","SE"]<-round(closedN.3$seNhat[3],2)
Mark.Table[Mark.Table$Period==3 & Mark.Table$Model=="Mh","SE"]<-round(closedN.3$seNhat[4],2)

Mark.Table[Mark.Table$Period==3 & Mark.Table$Model=="M0","Min"]<-round(closedN.3$lclNhat[1],0)
Mark.Table[Mark.Table$Period==3 & Mark.Table$Model=="Mb","Min"]<-round(closedN.3$lclNhat[2],0)
Mark.Table[Mark.Table$Period==3 & Mark.Table$Model=="Mt","Min"]<-round(closedN.3$lclNhat[3],0)
Mark.Table[Mark.Table$Period==3 & Mark.Table$Model=="Mh","Min"]<-round(closedN.3$lclNhat[4],0)

Mark.Table[Mark.Table$Period==3 & Mark.Table$Model=="M0","Max"]<-round(closedN.3$uclNhat[1],0)
Mark.Table[Mark.Table$Period==3 & Mark.Table$Model=="Mb","Max"]<-round(closedN.3$uclNhat[2],0)
Mark.Table[Mark.Table$Period==3 & Mark.Table$Model=="Mt","Max"]<-round(closedN.3$uclNhat[3],0)
Mark.Table[Mark.Table$Period==3 & Mark.Table$Model=="Mh","Max"]<-round(closedN.3$uclNhat[4],0)

# Add info in Mark.Table Period = 5
Mark.Table[Mark.Table$Period==5 & Mark.Table$Model=="M0","AIC"]<-round(closedN.5$AIC[1],0)
Mark.Table[Mark.Table$Period==5 & Mark.Table$Model=="Mb","AIC"]<-round(closedN.5$AIC[2],0)
Mark.Table[Mark.Table$Period==5 & Mark.Table$Model=="Mt","AIC"]<-round(closedN.5$AIC[3],0)
Mark.Table[Mark.Table$Period==5 & Mark.Table$Model=="Mh","AIC"]<-round(closedN.5$AIC[4],0)

Mark.Table[Mark.Table$Period==5 & Mark.Table$Model=="M0","N"]<-round(closedN.5$Nhat[1],0)
Mark.Table[Mark.Table$Period==5 & Mark.Table$Model=="Mb","N"]<-round(closedN.5$Nhat[2],0)
Mark.Table[Mark.Table$Period==5 & Mark.Table$Model=="Mt","N"]<-round(closedN.5$Nhat[3],0)
Mark.Table[Mark.Table$Period==5 & Mark.Table$Model=="Mh","N"]<-round(closedN.5$Nhat[4],0)

Mark.Table[Mark.Table$Period==5 & Mark.Table$Model=="M0","SE"]<-round(closedN.5$seNhat[1],2)
Mark.Table[Mark.Table$Period==5 & Mark.Table$Model=="Mb","SE"]<-round(closedN.5$seNhat[2],2)
Mark.Table[Mark.Table$Period==5 & Mark.Table$Model=="Mt","SE"]<-round(closedN.5$seNhat[3],2)
Mark.Table[Mark.Table$Period==5 & Mark.Table$Model=="Mh","SE"]<-round(closedN.5$seNhat[4],2)

Mark.Table[Mark.Table$Period==5 & Mark.Table$Model=="M0","Min"]<-round(closedN.5$lclNhat[1],0)
Mark.Table[Mark.Table$Period==5 & Mark.Table$Model=="Mb","Min"]<-round(closedN.5$lclNhat[2],0)
Mark.Table[Mark.Table$Period==5 & Mark.Table$Model=="Mt","Min"]<-round(closedN.5$lclNhat[3],0)
Mark.Table[Mark.Table$Period==5 & Mark.Table$Model=="Mh","Min"]<-round(closedN.5$lclNhat[4],0)

Mark.Table[Mark.Table$Period==5 & Mark.Table$Model=="M0","Max"]<-round(closedN.5$uclNhat[1],0)
Mark.Table[Mark.Table$Period==5 & Mark.Table$Model=="Mb","Max"]<-round(closedN.5$uclNhat[2],0)
Mark.Table[Mark.Table$Period==5 & Mark.Table$Model=="Mt","Max"]<-round(closedN.5$uclNhat[3],0)
Mark.Table[Mark.Table$Period==5 & Mark.Table$Model=="Mh","Max"]<-round(closedN.5$uclNhat[4],0)

# IC in one column:
Mark.Table$IC<-paste(Mark.Table$Min,Mark.Table$Max,sep="-")
Mark.Table$Min<-NULL
Mark.Table$Max<-NULL

#Order by AIC and period
Mark.Table.3<-Mark.Table[Mark.Table$Period==3,]
Mark.Table.3<-Mark.Table.3[order(Mark.Table.3$AIC),]

Mark.Table.5<-Mark.Table[Mark.Table$Period==5,]
Mark.Table.5<-Mark.Table.5[order(Mark.Table.5$AIC),]

Mark.Table<-rbind(Mark.Table.3,Mark.Table.5)

#Add An external model result to Mark.Table
if(length(External.Model)>1){
  Mark.Table.exct<-data.table(Period=External.Model[1],
                       Model=External.Model[2],
                       AIC="Ext. Model",
                       N=External.Model[3],
                       SE=External.Model[4],
                       IC=External.Model[5])


  Mark.Table<-rbind(Mark.Table,Mark.Table.exct)
  
  Mark.Table$N<-as.numeric(Mark.Table$N)
  Mark.Table$SE<-as.numeric(Mark.Table$SE)
}


#Make a copy to have shorter code in inline code (for abstract):
Mark.Table.inline<-Mark.Table

#Mark.Table as a felxtable
Mark.Table<-flextable(Mark.Table)
Mark.Table <- set_caption(Mark.Table, caption = " Selection of the best model and estimation of the number of lynx.")
Mark.Table<-font(Mark.Table,fontname = "Calibri", part = "all")
Mark.Table<-fontsize(Mark.Table,size = 12, part = "body")


#In Bold the Best model (lower AIC in period category)
which.best.model.3<-which(Mark.Table$body$dataset$AIC== min(Mark.Table$body$dataset[Mark.Table$body$dataset$Period==3,"AIC"]))
which.best.model.5<-which(Mark.Table$body$dataset$AIC== min(Mark.Table$body$dataset[Mark.Table$body$dataset$Period==5,"AIC"]))

Mark.Table <- bold(Mark.Table, bold = TRUE, i=c(which.best.model.3,which.best.model.5))


#Change name to fit language
Mark.Table <- set_header_labels(Mark.Table,
                        values = list(Period = "Period",
                                      Model = "Model",
                                      AICc = "AIC",
                                      N = "N lynx",
                                      IC = "IC 95%"))

#Create footnote:

if(Language=="FR"){
 Mark.Table<- footnote( Mark.Table, i =1 ,j=2,part = "header",
            value = as_paragraph("M0: P. are constant
Mb: P. vary by behavioural response to capture
Mt: P. vary with time
Mh: P. vary by individual animal"),ref_symbols = c(""))

}

#Autofit (last to make sur it works)
Mark.Table<-autofit(Mark.Table)
Mark.Table<-height_all(Mark.Table, height = .26)
Mark.Table<- hrule(Mark.Table, rule = "exact")
Mark.Table<- hline(Mark.Table, i=4)

if(length(External.Model)>1){
  Mark.Table<- hline(Mark.Table, i=8)
}


```

```{r table Opp. mon,echo=FALSE}

# Import Lynx Observation Data
Data.opp<-data.table::fread(LynxObs,select=(c("lynx_ID","date","type","x","y","canton","SCALP","fk_case_id")))
Data.opp$date<-as.POSIXct(Data.opp$date,  format= '%Y-%m-%d' )
  
#Subset data Session window
Data.opp<-Data.opp[Data.opp$date>Start & Data.opp$date<Stop,]
  
#Observations as spatial points
pts <- sf::st_as_sf(Data.opp, coords = c("x","y"))
pts <-sf::st_set_crs(pts, 21781) 
  
#Import shapefile reference area
Refareashp <- sf::read_sf(dsn = "MAP_Data/Reference_areas_alln.shp")
  
#Subset observation within the reference area
#Warnings ok
suppressWarnings(pts<-sf::st_intersection(pts,Refareashp$geometry[Refarea]))
  

#Sort data Opp. Mon.
pts<-as.data.table(pts)
pts<-pts[,c("fk_case_id","date","type","lynx_ID","canton","SCALP")]

Opp.table<-data.table(ID=sort(unique(pts$lynx_ID)))

if(length(Opp.table$ID)>0){
  for(i in 1:length(Opp.table$ID)){
    Opp.table[i,"Event"]<-length(unique(pts[pts$lynx_ID==Opp.table[i,ID],fk_case_id]))
    Opp.table[i,"Min.date"]<-min(pts[pts$lynx_ID==Opp.table[i,ID],date])
    Opp.table[i,"Max.date"]<-max(pts[pts$lynx_ID==Opp.table[i,ID],date])
    Opp.table[i,"Canton"]<-paste(unique(pts[pts$lynx_ID==Opp.table[i,ID],canton]),collapse=", ")
  }
}else{warning("No opp. mon. observations")}

Opp.table$Max.date<-as.character(Opp.table$Max.date)
Opp.table$Min.date<-as.character(Opp.table$Min.date)

#Any lynx not seen in det. mon. but seen in opp. mon:
Opp.table$line<-1:length(Opp.table$ID)
Not.seen<-Opp.table[!grepl(paste(unique(Data[Data$animal_species=="Lynx lynx" & Data$TIME>Start & Data$TIME<Stop,id_individual]), collapse="|"),
      Opp.table$ID),which = FALSE]
Opp.table$line<-NULL


#Change name to fit language
names(Opp.table)<-c("ID","Event","Date min.","Date max.","Canton")

#Transform data.table into flextable with legend and font
Opp.table<-flextable(Opp.table)
Opp.table<-autofit(Opp.table)
Opp.table <- set_caption(Opp.table, caption = " Opportunistic observations that took place during the monitoring period and were transmitted to KORA. An event can be represented by several images taken at the same place and time.")
Opp.table<-font(Opp.table,fontname = "Calibri", part = "all")
Opp.table<-fontsize(Opp.table,size = 12, part = "body")
Opp.table<-height_all(Opp.table, height = .26)
Opp.table<- hrule(Opp.table, rule = "exact")
Opp.table <- bold(Opp.table, bold = TRUE, i=Not.seen[,line])

#Create footnote:
if(length(Not.seen$line)>0){
  Opp.table<- footnote( Opp.table, i = Not.seen[,line],j=1,
            value = as_paragraph("Lynx observed opportunistically but not observed in the deterministic session are in bold."),ref_symbols = c("1"))
}

if(length(Not.seen$line)==0){
  Opp.table<- footnote( Opp.table, i = 1,j=1,
            value = as_paragraph("All opportunistically observed lynxes were also observed in the deterministic session."),ref_symbols = c("1"),part = "header")
}

```

```{r abstract number automatic 2nd part, echo=FALSE}

# ---- Compute Density 

# - Needed values:
N<-Mark.Table.inline[which.best.model.selected,N]
SE<-Mark.Table.inline[which.best.model.selected,SE]
Surface<-round(Refareashp$AREA_1[Refarea]/1000000,0)

# Density per 100 km2
Density.surface<-100*(N/Surface)
Density.surface.min95<-round(Density.surface-((SE/Surface)*100)*1.962,2)
Density.surface.max95<-round(Density.surface+((SE/Surface)*100)*1.962,2)
Density.surface<-round(Density.surface,2)

# Density per 100 km2 suitable habitat
Density.surface.favorable<-100*(N/favorable)
Density.surface.favorable.min95<-round(Density.surface.favorable-((SE/favorable)*100)*1.962,2)
Density.surface.favorable.max95<-round(Density.surface.favorable+((SE/favorable)*100)*1.962,2)
Density.surface.favorable<-round(Density.surface.favorable,2)


```

```{r Plot cumulative, echo=FALSE}

jpeg(filename = "Plot_cumulative.jpeg", width = 16.5, height = 8,
     units = "cm", quality = 100, bg = "white", res=1000)

par(mfrow=c(1,2))


par(mar=c(4,3,1,0))
  plot(Occ.table.plot.3$SUM.ID.cumulative, type="o", 
     xlab=NA,ylab=NA,col="blue",
     xaxt='n',las=1,cex.lab=0.8,cex.axis=0.8,pch=19,cex=1.5,lwd=1.5,
     xlim=c(1,20),
     #ylim based on period 5 in case higher:
     ylim=c(0,10^ceiling(log10(max(Occ.table.plot.5$SUM.occasion.cumulative))))) 
  axis(side=1,at=c(1,5,10,15,20),labels = c(1,5,10,15,20),cex.axis=0.8)
  mtext(side=1,"Occasions", line= 2,cex=0.8)
  mtext(side=2,"Captures", line= 2,cex=0.8)
  par(new=TRUE)
  plot(Occ.table.plot.3$SUM.occasion.cumulative, type="o", 
     xlab = NA,ylab=NA,pch=17,
     axes=FALSE,lwd=1.5,cex=1.5,
     xlim=c(1,20),ylim=c(0,10^ceiling(log10(max(Occ.table.plot.5$SUM.occasion.cumulative)))))
  legend("topleft",paste("Closure Test: Otis et al. (1978), p=",round(closure.result.3$Otis$p,3),
"
Occasion = 3 jours
"),cex=0.6)

par(mar=c(4,0.5,1,0.5))
  plot(Occ.table.plot.5$SUM.ID.cumulative, type="o", 
     xlab=NA,ylab="Captures",col="blue",
     xaxt='n',las=1,cex.lab=0.8,cex.axis=0.8,pch=19,cex=1.5,lwd=1.5,
     axes=FALSE,
     xlim=c(1,12),ylim=c(0,10^ceiling(log10(max(Occ.table.plot.5$SUM.occasion.cumulative)))))
  box()
  axis(side=1,at=c(1:12),labels = c(1:12),cex.axis=0.8)
  mtext(side=1,"Occasions", line= 2,cex=0.8)
  par(new=TRUE)
  plot(Occ.table.plot.5$SUM.occasion.cumulative, type="o", 
     xlab = NA,ylab=NA,pch=17,
     axes=FALSE,lwd=1.5,cex=1.5,
     xlim=c(1,12),ylim=c(0,10^ceiling(log10(max(Occ.table.plot.5$SUM.occasion.cumulative)))))
  legend("topleft",paste("Closure Test: Otis et al. (1978), p=",round(closure.result.5$Otis$p,3),
"
Occasion = 5 jours
"),cex=0.6)


invisible(dev.off())


### Select model Plot in Report

if(Period.selected==3){
  
  jpeg(filename = "Plot_cumulative_report.jpeg", width = 14, height = 8.5,
     units = "cm", quality = 100, bg = "white", res=1000)
  
  par(mar=c(2.5,2.5,0.5,0.5),mgp = c(0, 0.2, 0))
  plot(Occ.table.plot.3$SUM.ID.cumulative, type="o", 
     xlab=NA,ylab=NA,col="blue",
     xaxt='n',las=1,cex.lab=0.5,cex.axis=0.5,pch=19,cex=1.5,lwd=1.5,
     tck=-0.01,
     xlim=c(1,20),
     #ylim based on period 5 in case higher:
     ylim=c(0,10^ceiling(log10(max(Occ.table.plot.5$SUM.occasion.cumulative))))) 
  axis(side=1,at=c(1:20),labels = c(1:20),cex.axis=0.5,tck=-0.01)
  par(new=TRUE)
  plot(Occ.table.plot.3$SUM.occasion.cumulative, type="o", 
     xlab = NA,ylab=NA,pch=17,
     axes=FALSE,lwd=1.5,cex=1.5,
     xlim=c(1,20),ylim=c(0,10^ceiling(log10(max(Occ.table.plot.5$SUM.occasion.cumulative)))))
  grid(NA,NULL,lwd=1)
  
  if(Language=="FR"){
     mtext(side=1,"Occasions", line= 0.7,cex=1)
     mtext(side=2,"Captures", line= 0.6,cex=1)
     legend("topleft", legend=c("Captures cumulées", "Nombre de lynx capturés"),
       col=c("black", "blue"),pch=c(17,19), cex=1) 
  }

  if(Language=="DE"){
     mtext(side=1,"Triaden", line= 0.7,cex=1)
     mtext(side=2,"Erfassungen", line= 0.6,cex=1)
     legend("topleft", legend=c("Kumulierte Erfassungen", "Anzahl verschiedene Luchse"),
       col=c("black", "blue"),pch=c(17,19), cex=1) 
  }
  
  invisible(dev.off())
}

if(Period.selected==5){
  
  jpeg(filename = "Plot_cumulative_report.jpeg", width = 14, height = 8.5,
     units = "cm", quality = 100, bg = "white", res=1000)
  
  par(mar=c(2.5,2.5,0.5,0.5),mgp = c(0, 0.2, 0))
  plot(Occ.table.plot.5$SUM.ID.cumulative, type="o", 
     xlab=NA,ylab=NA,col="blue",
     xaxt='n',las=1,cex.lab=0.5,cex.axis=0.5,pch=19,cex=1.5,lwd=1.5,
     tck=-0.01,
     xlim=c(1,12),
     #ylim based on period 5 in case higher:
     ylim=c(0,10^ceiling(log10(max(Occ.table.plot.5$SUM.occasion.cumulative))))) 
  axis(side=1,at=c(1:12),labels = c(1:12),cex.axis=0.5,tck=-0.01)
  par(new=TRUE)
  plot(Occ.table.plot.5$SUM.occasion.cumulative, type="o", 
     xlab = NA,ylab=NA,pch=17,
     axes=FALSE,lwd=1.5,cex=1.5,
     xlim=c(1,12),ylim=c(0,10^ceiling(log10(max(Occ.table.plot.5$SUM.occasion.cumulative)))))
  grid(NA,NULL,lwd=1)
  
  if(Language=="FR"){
     mtext(side=1,"Occasions", line= 0.7,cex=1)
     mtext(side=2,"Captures", line= 0.6,cex=1)
     legend("topleft", legend=c("Captures cumulées", "Nombre de lynx capturés"),
       col=c("black", "blue"),pch=c(17,19), cex=1) 
  }

  if(Language=="DE"){
     mtext(side=1,"Pentaden", line= 0.7,cex=1)
     mtext(side=2,"Erfassungen", line= 0.6,cex=1)
     legend("topleft", legend=c("Kumulierte Erfassungen", "Anzahl verschiedene Luchse"),
       col=c("black", "blue"),pch=c(17,19), cex=1) 
  }
  
  
  
  invisible(dev.off())
}





```

```{r Density comparaison Table, echo= FALSE}

History<-as.matrix(fread("Density_KORA_Historic_Values.csv",header = TRUE))

Komp.DE<-c("Nordostschweiz","Misox (Mesolcina)","Tessin","Surselva","Zentralschweiz Ost","Rhone-Nord","Unterwallisüd","Simme-Saane","Engadin","Jura Nord","Jura Süd","Mittelbünden", "Zentralschweiz West","Zentralschweiz Mitte","Berner Oberland Ost","Oberwallis")

Komp.FR<-c("Nord-Est de la Suisse","Misox (Mesolcina)","Tessin","Surselva","Est de la Suisse centrale","Nord du Rhône","Sud du Bas-Valais", "Simme-Saane", "Engadin", "Nord du Jura","Sud du Jura", "Centre des Grisons","Ouest de la Suisse centrale", "Centre de la Suisse centrale","l'Est de l'Oberland-Bernois","Haut-Valais")

if(Language=="FR"){
  History.comparaison<-data.table(Compartment=Komp.FR)
}
if(Language=="DE"){
  History.comparaison<-data.table(Compartment=Komp.DE)
}

History.comparaison$COMPID<-c("II","Vb","Va","Vc","IIIc","IVc","IVd","IVa","Ve","Ib","Ia","Vd","IIIa","IIIb","IVb","IVe")

for(i in 1:length(History.comparaison$Compartment)){
  
  list.comp<-tail(as.character(na.omit(History[,i+1])),n=1)
  if(length(list.comp)>0){
  History.comparaison[i,"Winter"]<-History[which(History == list.comp, arr.ind=T)[,"row"],1]
  History.comparaison[i,"Density"]<-as.numeric(substr(list.comp, 1, 4))
  History.comparaison[i,"IC95"]<-paste("(",as.numeric(substr(list.comp, 7, 10)),"-",as.numeric(substr(list.comp, 12, 15)),")",sep="")
  
  }else{History.comparaison[i,"Winter"]<-"Pas de session"}

}

#Compute current values

Current<-data.table(Year=paste(min(year(occasions)),max(year(occasions)),sep="/"),
                    Density=Density.surface.favorable, 
                    Min95=Density.surface.favorable.min95,
                    Max95=Density.surface.favorable.max95)


#Add new value of this session
History.comparaison<-as.data.frame(History.comparaison)
History.comparaison[Compartment,"Winter"]<-Current[,Year]
History.comparaison[Compartment,"Density"]<-Current[,Density]
History.comparaison[Compartment,"IC95"]<-paste("(",Current[,Min95],"-",Current[,Max95],")", sep="")
History.comparaison<-as.data.table(History.comparaison)

#Set order COMPID (alphabetic order does not work->manual)
History.comparaison<-History.comparaison[c(11,10,1,13,14,5,8,15,6,7,16,3,2,4,12,9),]

#Set order Density
History.comparaison<-History.comparaison[order(History.comparaison$Density,decreasing=TRUE,na.last=TRUE),]

#Get position actual session:
line.session<-History.comparaison[COMPID==names(Text.table)[Refarea+1],which=TRUE]
#Get position for (NA-NA) sessions:
line.NA<-History.comparaison[COMPID=="IVe"|COMPID=="IVd",which=TRUE]

#change "." to ","
for(i in 1:nrow(History.comparaison)){
  History.comparaison[i,"Density_text"]<-prettyNum(History.comparaison[i,Density],decimal.mark = ",")
  History.comparaison[i,"IC95"]<-gsub("[.]", ",", History.comparaison[i,IC95])
}

#reset order column:
History.comparaison$Density<-NULL
names(History.comparaison)[5]<-"Density"
History.comparaison<-History.comparaison[,c("COMPID","Compartment","Winter","Density","IC95")]

#Set name columns (FR/DE)
if(Language=="FR"){
  names(History.comparaison)<-c("ID Comp.","Aire de référence","Hiver","Densité","IC 95% ")
}
if(Language=="DE"){
  names(History.comparaison)<-c("ID Komp.","Referenzgebiet","Winter","Dichte","95% KI")
}

#Transform data.table into flextable with legend and font
History.comparaison<-flextable(History.comparaison)
History.comparaison<-autofit(History.comparaison)

if(Language=="FR"){
  History.comparaison <- set_caption(History.comparaison, caption = "Pour chacune des 16 aires de référence officielles figure l’estimation de la densité estimée de lynx (lynx indépendants pour 100 km^2^ d’habitat favorable) avec intervalle de confiance de 95% de da dernière session, à l'exception de celles où le lynx n'y est pas encore présent en nombre suffisant pour justifier cette méthode. Les densités sont classées par ordre décroissant. En gras/ : les valeurs de la session traitée dans le présent rapport. Les sous-compartiments sont présentés à la Fig. 1.",autonum = officer::run_autonum(
  seq_id = "table",
  pre_label = "Tab. ",
  post_label = ". ",
  bkm = NULL,
  bkm_all = FALSE,
  prop = officer::fp_text(bold= TRUE, font.size = 12, font.family= "Calibri") ,
  start_at = ""
))
}

if(Language=="DE"){
  History.comparaison <- set_caption(History.comparaison, caption = "Geschätzte Dichten von unabhängigen Luchsen pro 100 km^2^ günstigen Lebensraums aus den letzten Sitzungen für die 16 offiziellen Referenzgebiete. In einigen Referenzgebieten wurde nie ein deterministisches Monitoring durchgeführt, da die Luchse nicht in ausreichender Zahl vorhanden sind, um diese Methode zu rechtfertigen. Die Fächer sind in Abb. 1 dargestellt.",autonum = officer::run_autonum(
  seq_id = "table",
  pre_label = "Tab. ",
  post_label = ". ",
  bkm = NULL,
  bkm_all = FALSE,
  prop = officer::fp_text(bold= TRUE, font.size = 12, font.family= "Calibri") ,
  start_at = ""
))
}

#Create footnote:
if(Language=="FR"){
  History.comparaison<- footnote( History.comparaison, i = line.NA,j=5,
            value = as_paragraph("NA figure lorsque l’abondance et par la même la précision n’ont pas pu être estimées au moyen de la méthode de capture-recapture photographique car le nombre de lynx est trop faible."),ref_symbols = c("*"),part = "body")
}

if(Language=="DE"){
  History.comparaison<- footnote( History.comparaison, i = line.NA,j=5,
            value = as_paragraph("NA-Zahl, wenn die Abundanz und damit die Genauigkeit nicht mit der fotografischen Fang-Wiederfang-Methode geschätzt werden konnte, weil die Zahl der Luchse zu gering ist."),ref_symbols = c("*"),part = "body")
}

History.comparaison<-bold(History.comparaison, i = line.session, j = NULL, bold = TRUE, part = "body")

History.comparaison<-font(History.comparaison,fontname = "Calibri", part = "all")
History.comparaison<-fontsize(History.comparaison,size = 12, part = "body")
History.comparaison<-height_all(History.comparaison, height = .27)
History.comparaison<- hrule(History.comparaison, rule = "exact")


```

```{r History , echo=FALSE}

#History Table

History<-fread("Density_KORA_Historic_Values.csv",header = TRUE,select=c("Year",as.character(Compartment)))

History<-na.omit(History,cols = as.character(Compartment))

for(i in 1:length(History$Year)){
  History[i,"Density"]<-as.numeric(substr(as.character((History[i,2])), 1, 4))
  History[i,"Min95"]<-as.numeric(substr(as.character((History[i,2])), 7, 10))
  History[i,"Max95"]<-as.numeric(substr(as.character((History[i,2])), 12, 15))
}

# Add current Monitoring values to history plot:
#Object current is created in Density comparaison

History[,2]<-NULL

History<-rbind(History,Current)

# Error bar
History.plot<-ggplot2::ggplot(History) +
              ggplot2::geom_bar( ggplot2::aes(x=Year, y=Density), stat="identity",
                                 fill=c(rep("#009E73",length(History$Year)-1),"#E69F00"),
                                 alpha=1) +
              ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45,hjust = 1),
                             axis.title.x=ggplot2::element_blank())+
              ggplot2::geom_errorbar( ggplot2::aes(x=Year, ymin=Min95, ymax=Max95),
                                      width=0.08, colour="black", alpha=0.9, size=0.5)+ggplot2::theme_bw()+
              ggplot2::geom_text(ggplot2::aes(y = 0.4,x=1:length(History$Year)),
                                              label=History$Density, vjust = 0, nudge_y = 0,size=3)+
              ggplot2::geom_text(ggplot2::aes(y = 0,x=1:length(History$Year)),
                                              label=paste("(",History$Min95,"-",History$Max95,")",sep=""),
                                              vjust = 0, nudge_y = .2,size=3)+
              ggplot2::scale_y_continuous(breaks = seq(0,6,by=0.5),
                                          minor_breaks=NULL) 


#Add label
if(Language=="FR"){
History.plot<-History.plot+ggplot2::xlab("Hiver")+ggplot2::ylab("Densité")
}

if(Language=="DE"){
History.plot<-History.plot+ggplot2::xlab("Winter")+ggplot2::ylab("Dichte")
}


ggplot2::ggsave("History_denisty_plot.jpeg",plot=History.plot,
                    units = "cm",
                    width = 16.5,
                    height = 8.5)
```

```{r Plot CH (Introduction), echo=FALSE}

#Import shapefile compartment
Komp <- sf::read_sf(dsn = "MAP_Data/Luchs_Komp_21_07_2015_new.shp")


# -- Altitude layer #
Alt <- raster::raster("MAP_Data/CHHS.TIF")
# indicate CRS
raster::crs(Alt) <- CRS 
# convert to a df for plotting in two steps:
# First, to a SpatialPointsDataFrame
Alt_pts <- raster::rasterToPoints(Alt, spatial = TRUE)

# -- Use ingfo to compute Study Area 
study_area<-sp::bbox(Alt_pts)
study_area<-rgeos::readWKT(paste("POLYGON((",
                                   study_area[1,1]," ",study_area[2,1],",",
                                   study_area[1,1]," ",study_area[2,2],",",
                                   study_area[1,2]," ",study_area[2,2],",",
                                   study_area[1,2]," ",study_area[2,1],",",
                                   study_area[1,1]," ",study_area[2,1],"))",sep=""),p4s= CRS)

# Then convert SpatialPointsDataFrame to a 'conventional' dataframe
Alt_df  <- data.frame(Alt_pts)
rm(Alt_pts, Alt)

# -- Suitable habitat layer #
suppressWarnings(Suitable <- raster::raster("MAP_Data/suitable_CH1.tif"))
# indicate CRS
raster::crs(Suitable) <- CRS 
# crop 
Suitable<-raster::crop(Suitable,study_area)
# convert to a df for plotting in two steps:
# First, to a SpatialPointsDataFrame
Suitable_pts <- raster::rasterToPoints(Suitable, spatial = TRUE)
# Then to a 'conventional' dataframe
Suitable_df  <- data.frame(Suitable_pts)
rm(Suitable_pts, Suitable)
  
# -- Import shapefile lakes
suppressWarnings(Lakes <- raster::shapefile("MAP_Data/grandlacs.shp"))
Lakes<-raster::crop(Lakes,study_area)
Lakes<-sf::st_as_sf(Lakes)

#Import shapefile white background
Mask <- suppressWarnings(raster::shapefile("MAP_Data/Mask_CH_Liechtenstein.shp"))
Mask<-raster::crop(Mask,study_area)
Mask<-sf::st_as_sf(Mask)

# --- Import shapefile Study area Polygon
suppressWarnings(Rcompartment <- raster::shapefile("MAP_Data/Reference_areas_alln.shp"))
Rcompartment<-sf::st_as_sf(Rcompartment)
  
map<-ggplot2::ggplot() +
  #Alt Raster
  ggplot2::geom_raster(data = Alt_df , ggplot2::aes(x = x, y = y, alpha = CHHS))+ 
  ggplot2::scale_alpha(name = "", range = c(0.6, 0))+
  #Background white
  ggplot2::geom_sf(data=Mask,fill="white")+
  #Suitable Raster
  ggplot2::geom_tile(data = Suitable_df , ggplot2::aes(x = x, y = y),fill="yellowgreen", alpha = 0.4)+
  #Polygon Compartment all
  ggplot2::geom_sf(data=Komp$geometry,colour = "black",fill="NA",lwd=0.6)+
  #Polygon Compartment
  ggplot2::geom_sf(data=Komp$geometry[Compartment],fill="white", alpha = 0.4)+
  #Polygon Compartment all text
  ggplot2::geom_sf_text(data=Komp,ggplot2::aes(label =  Nummer))+
  #Lakes
  ggplot2::geom_sf(data=Lakes,fill="#56B4E9")+
  #Reference Area all
  ggplot2::geom_sf(data=Rcompartment,col="darkblue",fill=NA,lwd=0.5)+
  #Reference Area
  ggplot2::geom_sf(data=Rcompartment[Refarea,],col="darkblue",fill=NA,lwd=1.1)


  #Theme
  map<-map+ggplot2::theme(plot.title =ggplot2::element_blank(),
        strip.background = ggplot2::element_blank(),
        panel.background = ggplot2::element_blank(),
        panel.grid = ggplot2::element_blank(),
        axis.title =ggplot2::element_blank(),
        axis.text = ggplot2::element_blank(),
        axis.ticks= ggplot2::element_blank(),
        legend.position="none",
        panel.border = ggplot2::element_rect(colour = "black", fill=NA, size=0.1))+
        ggplot2::scale_x_continuous(expand = c(0, 0)) +
        ggplot2::scale_y_continuous(expand = c(0, 0))
  

  
  # --- Add KORA GIS Logo:
  img <- png::readPNG("KORAlogo.png")#KoraGis_transp
  g <- grid::rasterGrob(img, interpolate=TRUE)
  
  map<-map+
  ggplot2::annotation_custom(g, xmin=study_area[1]@bbox[1,2]-40000, xmax=study_area[1]@bbox[1,2],
                               ymin=study_area[1]@bbox[2,1], ymax=study_area[1]@bbox[2,1]+40000)
  
  
  ggplot2::ggsave("Plot_Introduction_Compartment.jpeg",plot=map,
                    units = "cm",
                    width = 16.5,
                    height = 10.3)
  



```

```{r Plot reference Area (Introduction), echo=FALSE}

#Import shapefile compartment
Komp <- sf::read_sf(dsn = "MAP_Data/Luchs_Komp_21_07_2015_new.shp")
  
# -- Study Area ####
study_area<-sp::bbox(as.matrix(Komp$geometry[Compartment][[1]]))
study_area.origin<-sp::bbox(as.matrix(Komp$geometry[Compartment][[1]]))
#Add x% around the BBox to have some extra map area
  
  study_area[1,1]<-study_area[1,1]-round(study_area[1,1]*0.02) #x min
  study_area[2,1]<-study_area[2,1]-round(study_area[2,1]*6*0.02) #y min
  study_area[1,2]<-study_area[1,2]+round(study_area[1,2]*0.02) #x max
  study_area[2,2]<-study_area[2,2]+round(study_area[2,2]*0.02) #y max
  
study_area<-rgeos::readWKT(paste("POLYGON((",
                                   study_area[1,1]," ",study_area[2,1],",",
                                   study_area[1,1]," ",study_area[2,2],",",
                                   study_area[1,2]," ",study_area[2,2],",",
                                   study_area[1,2]," ",study_area[2,1],",",
                                   study_area[1,1]," ",study_area[2,1],"))",sep=""),p4s= CRS)
    
# -- Suitable habitat layer #
suppressWarnings(Suitable <- raster::raster("MAP_Data/suitable_CH1.tif"))
# indicate CRS
raster::crs(Suitable) <- CRS 
# crop 
Suitable<-raster::crop(Suitable,study_area)
# convert to a df for plotting in two steps:
# First, to a SpatialPointsDataFrame
Suitable_pts <- raster::rasterToPoints(Suitable, spatial = TRUE)
# Then to a 'conventional' dataframe
Suitable_df  <- data.frame(Suitable_pts)
rm(Suitable_pts, Suitable)
  

# --- Import shapefile Study area Polygon
suppressWarnings(Rcompartment <- raster::shapefile("MAP_Data/Reference_areas_alln.shp"))
Rcompartment<-Rcompartment[Refarea,]

#Import shapefile compartment
suppressWarnings(Komp <- raster::shapefile("MAP_Data/Luchs_Komp_21_07_2015_new.shp"))
Komp<-Komp[Compartment,]

# ------ Open Source Map#### !!! Study area comes fromr Plot CH (Introduction)
  
#study area BBox in lat long
study_area_lat_long <- sp::spTransform(study_area, sp::CRS("+init=epsg:4326"))
  
  LAT1 = study_area_lat_long@bbox[2,1] ; LAT2 = study_area_lat_long@bbox[2,2]
  LON1 = study_area_lat_long@bbox[1,1] ; LON2 = study_area_lat_long@bbox[1,2]
  
#Get the map
#warnings OK
suppressWarnings(map <- OpenStreetMap::openmap(c(LAT2,LON1), c(LAT1,LON2), zoom = 10, #can be replaced by NULL
                                                 type = c("stamen-terrain")[1],
                                                 mergeTiles = TRUE))
  
#Correct projection
#warnings OK
suppressWarnings(map <- OpenStreetMap::openproj(map, projection = "+init=epsg:21781"))
  
# ------ Build map 

# --- Open Source Map in ggplot:
map<-OpenStreetMap::autoplot.OpenStreetMap(map)+
ggplot2::theme(axis.title=ggplot2::element_blank(),
                   axis.text=ggplot2::element_blank(),
                   axis.ticks=ggplot2::element_blank(),
                   panel.border = ggplot2::element_rect(colour = "white", fill=NA, size=12))


# --- Add Scale:
  
  # distance on x axes:
  dist.scale<-plyr::round_any(round(((study_area@bbox[1,2]-study_area@bbox[1,1])/1000)/4), 10, f = ceiling)
  
  # scale thickness:
  s.thick<-(0.01*(study_area@bbox[2,2]-study_area@bbox[2,1]))
  
  # scale black rectangle
  xleft<-study_area@bbox[1,1]+((study_area.origin[1,1]-study_area@bbox[1,1])/3)#left
  xright<-xleft+dist.scale*1000#right
  ybottom<-study_area.origin[2,1]-4*s.thick#bottom
  ytop<-study_area.origin[2,1]-3*s.thick#top

  map<-map+
    ggplot2::geom_rect(mapping=ggplot2::aes(xmin=xleft, xmax=xright, ymin=ybottom, ymax=ytop),
                       fill=c("black"),
                       inherit.aes = FALSE)+
    ggplot2::geom_text(x=xright+(2/5)*dist.scale*1000, y=ytop, label=paste(dist.scale,"Km",sep=" "), cex=4, color ="black")

  
# --- Add other layers:

map<-map+
#KOMP
ggplot2::geom_polygon(data = Komp@polygons[[1]], ggplot2::aes(x=long, y=lat,group = group),
                               colour="black", fill="white", alpha=0.4, lwd=1.1)+
#Suitable Raster
ggplot2::geom_tile(data = Suitable_df , ggplot2::aes(x = x, y = y),fill="yellowgreen", alpha = 0.6)+
#Refarea
ggplot2::geom_polygon(data = Rcompartment@polygons[[1]], ggplot2::aes(x=long, y=lat),
                               colour="darkblue", fill=NA, alpha=1, lwd=1.1)+
#Points Sites
ggplot2::geom_point(data=DataFULL,ggplot2::aes(x,y), col="white", pch=19,cex=2)+
      ggplot2::geom_point(data=DataFULL,ggplot2::aes(x,y),col="black", pch=1,cex=2)
  

ggplot2::ggsave("Plot_Introduction.jpeg",plot=map,
                    units = "cm",
                    width = 16.5,
                    height = 12)
  

```

```{r Dispersal check, echo=FALSE}

#check if any lynx of the table (Event.report) was once seen far away (> 150 km)

Dispersal<-data.table(ID=Lynx.Table.Adult$ID)

distfunction<-function(x1,x2,y1,y2){
  ((x1-x2)^2+(y1-y2)^2)^0.5
}

for(i in 1:nrow(Dispersal)){
  Dispersal[i,"Lastx"]<-tail(Data[Data$id_individual==Dispersal[i,ID],],1)[,31]
  Dispersal[i,"Lasty"]<-tail(Data[Data$id_individual==Dispersal[i,ID],],1)[,32]
  
  #Check longest distance in Photo Predator:
  loop1<-PhotoPredator.table[PhotoPredator.table$id_individual==Dispersal[i,ID],]
  for(j in 1:nrow(loop1)){
    loop1[j,"Dist"]<-distfunction(Dispersal[i,Lastx],loop1[j,x],Dispersal[i,Lasty],loop1[j,y])
  }
  Dispersal[i,"PP"]<-round(max(loop1$Dist),0)
  Dispersal[i,"PP.x"]<-unique(loop1[loop1$Dist==max(loop1$Dist),x])
  Dispersal[i,"PP.y"]<-unique(loop1[loop1$Dist==max(loop1$Dist),y])
  
  
  #Check longest distance in Lynx Obs:
  loop2<-LynxObs.table[LynxObs.table$lynx_ID==Dispersal[i,ID],]
  
  if(length(loop2$lynx_ID)>0){
    
  for(k in 1:nrow(loop2)){
  loop2[k,"Dist"]<-distfunction(Dispersal[i,Lastx],loop2[k,x],Dispersal[i,Lasty],loop2[k,y])
  }
  Dispersal[i,"LO"]<-round(max(loop2$Dist),0)
  Dispersal[i,"LO.x"]<-unique(loop2[loop2$Dist==max(loop2$Dist),x])
  Dispersal[i,"LO.y"]<-unique(loop2[loop2$Dist==max(loop2$Dist),y])
  
  }
 
  if(length(loop2$lynx_ID)>0){
  Dispersal[i,"MaxDist"]<-round(max(max(loop1$Dist),max(loop2$Dist)),0)
  }else{Dispersal[i,"MaxDist"]<-round(max(loop1$Dist),0)}
  
  
}

Dispersal<-Dispersal[order(Dispersal$MaxDist,decreasing=TRUE),]

#Dispersal as a flextable:
Dispersal<-flextable(Dispersal)
Dispersal <- set_caption(Dispersal, caption = "Dispersal table. This table give an indication of the longest distance between the last observation of a given lynx in the session and the entire KORA data base (Photo Predator + Lynx observations). If the distance is big, please check if it is a dispersal case. PP= Photo Predator's table, LO = Lynx Observations' table. Decreasing order from column MaxDist. [Unit = meters]")
Dispersal<-font(Dispersal,fontname = "Calibri", part = "all")
Dispersal<-autofit(Dispersal)




```

<br>

<br>

<br>

<br>

<br>

<br>

<br>

<br>

<br>


```{r Title, results = 'asis',echo=FALSE}
cat(paste("#",Title,sep=" "))
```

<br>

```{r Authors, results = 'asis',echo=FALSE}
cat(paste("##",Authors, sep=" "))
```

\newpage

```{r Abstract,echo=FALSE,results='asis'}

#Prepare sentence difference CI:
if(length(History$Year)==1){
   DifferentFR<-paste("**Il s'agit de la première estimation de densité pour cette aire de référence.**")
   DifferentDE<-paste("**Dies ist die erste Dichteschätzung für dieses Referenzgebiet.**")
   DifferentEN<-paste("**This is the first density estimate for this reference area.**")
  
  }else{
    smaller = (History[nrow(History)-1,Min95]>History[nrow(History),Max95])
    bigger = (History[nrow(History)-1,Max95]<History[nrow(History),Min95])
    
    if(smaller == FALSE & bigger == FALSE){
         DifferentFR<-paste("**La densité estimée n’a pas changé significativement par rapport à la valeur estimée lors de la dernière session.**")
         DifferentDE<-paste("**Die Dichte weicht nicht signifikant vom letzten geschätzten Wert ab.**")
         DifferentEN<-paste("**The estimated density has not changed significantly from the value estimated in the last session.**")
    }
    
    if(smaller == TRUE){
         DifferentFR<-paste("**La densité estimée est significativement plus basse par rapport à la valeur estimée lors de la dernière session.**")
         DifferentDE<-paste("**Die geschätzte Dichte ist signifikant niedriger als der in der letzten Sitzung geschätzte Wert.**")
         DifferentEN<-paste("**The estimated density is significantly lower than the value estimated in the last session.**")
    }
    
    if(bigger == TRUE){
         DifferentFR<-paste("**La densité estimée est significativement plus haute par rapport à la valeur estimée lors de la dernière session.**")
         DifferentDE<-paste("**Die geschätzte Dichte ist signifikant höher als der in der letzten Sitzung geschätzte Wert.**")
         DifferentEN<-paste("**The estimated density is significantly higher than the value estimated in the last session.**")
    }
}

#Build abstract (in 3 languages):
AbstractDE<-capture.output(cat("Das  Fotofallen-Monitoring  des  Luchses  (*Lynx lynx*) im  Referenzgebiet ", Text.table[1,Refarea+1],"  wurde im Winter ", paste(year(min(Data$TIME)), year(max(Data$TIME)),sep='/'),"  während  60  Nächten, vom ", paste(lubridate::day(Start),lubridate::month(Start),lubridate::year(Start),sep=".")," bis ", paste(lubridate::day(Stop),lubridate::month(Stop),lubridate::year(Stop),sep=".")," durchgeführt. Die Fotofallen an den ", Sites," Standorten funktionierten während ", prettyNum(effective.TN, big.mark="'",decimal.mark=",")," der potentiellen ", prettyNum(potentially.TN, big.mark="'",decimal.mark=",")," Fallen nächte (", gsub("[.]",",",sprintf("%.1f",round((effective.TN*100)/potentially.TN,1))),"%). Bei ", Event[ID=="Total",Event]," Ereignissen an ", Event[ID=="Total",`N site`]," Standorten  wurden ", N.ind.lynx," selbständige Luchse fotografiert. **Darüber hinaus wurden ", N.juv," Jungtier(e) aus mindestens ", length(unique(Lynx.Table[Lynx.Table$YOB==juv.year & Lynx.Table$mother!="",mother]))," Wurf/Würfen nachgewiesen.** Die Fang-Wiederfang Schätzung der Abundanz (95% Konfidenzintervall) nach dem Model M~", substr(Mark.Table.inline[which.best.model.selected,Model], 2, 2),"~ ergab ", Mark.Table.inline[which.best.model.selected,N]," (", gsub("[.]",",",sprintf("%.0f",round(Mark.Table.inline[which.best.model.selected,"N"]-1.96*Mark.Table.inline[which.best.model.selected,"SE"],0)))," - ", gsub("[.]",",",sprintf("%.0f",round(Mark.Table.inline[which.best.model.selected,"N"]+1.96*Mark.Table.inline[which.best.model.selected,"SE"],0))),") selbständige Luchse im Referenzgebiet, was einer Dichte von ", prettyNum(Density.surface.favorable,decimal.mark = ",")," (", prettyNum(Density.surface.favorable.min95,decimal.mark = ",")," - ", prettyNum(Density.surface.favorable.max95,decimal.mark = ","),") selbständigen Luchsen pro 100 km^2^ geeignetem Habitat entspricht. ",DifferentDE,sep = ""))

AbstractFR<-capture.output(cat("Le monitoring du lynx (*Lynx lynx*) par piège-photographique dans l'aire de référence ", Text.table[7,Refarea+1]," durant l’hiver ", paste(year(min(Data$TIME)), year(max(Data$TIME)),sep='/')," a été effectué durant 60 nuits du ", paste(lubridate::day(Start),lubridate::month(Start),lubridate::year(Start),sep=".")," au ", paste(lubridate::day(Stop),lubridate::month(Stop),lubridate::year(Stop),sep="."),". Les pièges-photos placés auprès des ", Sites," sites ont fonctionné pendant ", prettyNum(effective.TN, big.mark="'",decimal.mark=",")," des ", prettyNum(potentially.TN, big.mark="'",decimal.mark=",")," nuits potentielles (",  gsub("[.]",",",sprintf("%.1f",round((effective.TN*100)/potentially.TN,1))),"%). Dans l’aire de référence, ", Event[ID=="Total",Event]," évènements auprès de ", Event[ID=="Total",`N site`]," sites correspondant à ", N.ind.lynx," lynx indépendants ont été répertoriés. **De plus, ", N.juv," juvenile(s) d'au moins ", length(unique(Lynx.Table[Lynx.Table$YOB==juv.year & Lynx.Table$mother!="",mother]))," portée(s) ont également été détectés.** L’estimation de l’abondance (intervalle de confiance de 95%) par le modèle de capture-recapture M~", substr(Mark.Table.inline[which.best.model.selected,Model], 2, 2),"~ était de ", Mark.Table.inline[which.best.model.selected,N]," (", gsub("[.]",",",sprintf("%.0f",round(Mark.Table.inline[which.best.model.selected,"N"]-1.96*Mark.Table.inline[which.best.model.selected,"SE"],0)))," - ", gsub("[.]",",",sprintf("%.0f",round(Mark.Table.inline[which.best.model.selected,"N"]+1.96*Mark.Table.inline[which.best.model.selected,"SE"],0))),") lynx indépendants ce qui correspond à une densité de ", prettyNum(Density.surface.favorable,decimal.mark = ",")," (", prettyNum(Density.surface.favorable.min95,decimal.mark = ",")," - ", prettyNum(Density.surface.favorable.max95,decimal.mark = ","),") lynx indépendants pour 100 km^2^ d’habitat favorables. ",DifferentFR,sep = ""))

AbstractEN<-capture.output(cat("The monitoring of the Eurasian  lynx  (*Lynx lynx*)  by means of camera traps in the reference area ", Text.table[8,Refarea+1]," during  winter ", paste(year(min(Data$TIME)), year(max(Data$TIME)),sep='/')," was  carried  out  during 60  nights,  from  ", paste(lubridate::day(Start),lubridate::month(Start),lubridate::year(Start),sep="."),"  to  ", paste(lubridate::day(Stop),lubridate::month(Stop),lubridate::year(Stop),sep=".")," The camera traps at the ", Sites," locations operated during ", prettyNum(effective.TN, big.mark=",",decimal.mark=".")," of the potential ", prettyNum(potentially.TN, big.mark=",",decimal.mark=".")," trap nights (", sprintf("%.1f",round((effective.TN*100)/potentially.TN,1)),"%). During the session, ", Event[ID=="Total",Event]," events of ", N.ind.lynx," independent lynx at ", Event[ID=="Total",`N site`]," sites  were recorded. **In addition, ", N.juv," juvenile(s) of at least ", length(unique(Lynx.Table[Lynx.Table$YOB==juv.year & Lynx.Table$mother!="",mother]))," litter(s) were detected.** The capture-recapture estimate of abundance (95% confidence interval) under model M~",substr(Mark.Table.inline[which.best.model.selected,Model], 2, 2),"~ was ", Mark.Table.inline[which.best.model.selected,N]," (", gsub("[.]",",",sprintf("%.0f",round(Mark.Table.inline[which.best.model.selected,"N"]-1.96*Mark.Table.inline[which.best.model.selected,"SE"],0)))," - ", gsub("[.]",",",sprintf("%.0f",round(Mark.Table.inline[which.best.model.selected,"N"]+1.96*Mark.Table.inline[which.best.model.selected,"SE"],0))),") independent lynx, which corresponds to a density of  ", Density.surface.favorable," (", Density.surface.favorable.min95," - ", Density.surface.favorable.max95,") independent lynx per 100 km^2^ of suitable habitat. ",DifferentEN,sep = ""))

#Set Order abstract in the report:
if(Language=="FR"){

cat("### Résumé \n")
  
cat(AbstractFR)
cat("

\n

")

cat("### Zusammenfassung \n")

cat(AbstractDE)
cat("

\n

")

cat("### Abstract \n")

cat(AbstractEN)
cat("

\n

")

}

if(Language=="DE"){
  
cat("### Zusammenfassung \n")

cat(AbstractDE)
cat("

\n

")

cat("### Résumé \n")

cat(AbstractFR)
cat("

\n

")

cat("### Abstract \n")

cat(AbstractEN)
cat("

\n

")

}

```

\newpage

```{r Introduction FR,echo=FALSE,results='asis',eval=Language=="FR"}
cat("### Introduction \n")

cat("Le monitoring déterministe du lynx par pièges-photos a été développé en Suisse à partir de 1998 (Laas 1999) dans le nord-ouest des Alpes. Dans les sous-compartiments de gestion (voir [Plan Lynx Suisse OFEV 2016](https://www.kora.ch/uploads/media/F_Plan_Lynx_2016_Revision_des_annexes_2019.pdf)) dont l'habitat favorable pour le lynx est en grande partie colonisé de façon permanente par l’espèce, un suivi déterministe par pièges photos est effectué dans des aires dites de référence. Ces dernières sont choisies de sorte à ce qu’elles soient représentatives pour les sous-compartiments de gestion donnés (Fig. 1; voir [**ici**](https://www.kora.ch/index.php?id=240&L=2) pour plus d’informations). Au sein de chaque aire de référence des pièges-photos sont répartis de manière systématique et laissé en place pendant une période donnée, dans notre cas généralement pendant 60 nuits. Ce genre de suivi est conduit tous les trois à quatre ans par le KORA avec l’aide des cantons afin d’estimer la taille et la densité de la population de lynx au moyen de la méthode dite de capture-recapture photographique qui est aujourd’hui une méthode de monitoring standard pour le suivi des espèces aux mœurs cryptiques dont les individus sont reconnaissables au moyen de marques naturelles (voir [**ici**](https://www.kora.ch/index.php?id=105&L=2) pour plus d’informations).

Ce rapport présente les résultats de la session déterministe dans l'aire de référence ",Text.table[7,Refarea+1]," au sein du sous-compartiment ",names(Text.table)[Refarea+1]," pour l’hiver ", paste(year(min(Data$TIME)), year(max(Data$TIME)),sep='/'),". Les résultats des sessions précédentes sont disponibles [**en ligne**](https://www.kora.ch/index.php?id=345&L=2) sur le site du KORA.
\n",sep="")

cat("![**Fig. 1.** Répartition des aires de références (polygones bleus) au sein des 16 sous-compartiments de gestion (polygones noirs). En vert clair, l'habitat favorable du lynx défini par un modèle d'habitat (Zimmermann 2004, Zimmermann & Breitenmoser 2007). L'aire de références (",Text.table[7,Refarea+1],") ainsi que le sous-compartiment (",names(Text.table)[Refarea+1],") de gestion dans lesquels s'est déroulé cette session sont mis en évidence.](Plot_Introduction_Compartment.jpeg) 

\n",sep="")

```

```{r Introduction DE,echo=FALSE,results='asis',eval=Language=="DE"}
cat("### Einleitung \n")

cat("Ein deterministisches Luchsmonitoring mit Kamerafallen wird in der Schweiz seit 1998 (Laas 1999) in den Nordwestalpen entwickelt. In Teilkompartimenten (siehe [Konzept  Luchs Schweiz BAFU 2016](https://www.kora.ch/uploads/media/D_Konzept_Luchs_Schweiz_2016_Revision_Anhaenge_2019.pdf)), in denen der luchsfreundliche Lebensraum weitgehend dauerhaft von der Art besiedelt ist, wird ein deterministisches Monitoring mit Fotofallen in sogenannten Referenzgebieten durchgeführt. Diese sind so gewählt, dass sie für die jeweiligen Teilbereiche der Verwaltung repräsentativ sind (Abb. 1; weitere Informationen unter [**hier**] (https://www.kora.ch/index.php?id=240&L=0)). In jedem Referenzgebiet werden systematisch Fotofallen verteilt und für einen bestimmten Zeitraum, in unserem Fall in der Regel für 60 Nächte, stehen gelassen. Diese Art von Monitoring wird alle drei bis vier Jahre von KORA mit Hilfe der Kantone durchgeführt, um die Grösse und Dichte der Luchspopulation mittels der so genannten fotografischen Capture-Recapture-Methode abzuschätzen. Dies ist heute eine Standard-Monitoring-Methode für kryptische Arten, deren Individuen durch natürliche Markierungen erkennbar sind (siehe [**hier**] (https://www.kora.ch/index.php?id=105&L=0) für weitere Informationen)
    
Dieser Bericht enthält die Ergebnisse der deterministischen Sitzung im Referenzgebiet ",Text.table[1,Refarea+1]," innerhalb der Teilkompartiment ",names(Text.table)[Refarea+1]," für den Winter ", paste(year(min(Data$TIME)), year(max(Data$TIME)),sep='/'),". Die Ergebnisse der vorangegangenen Sitzungen sind [**online**] (https://www.kora.ch/index.php?id=345&L=0) auf der KORA-Website verfügbar.
\n",sep="")

cat("![**Abb. 1.** Verteilung der Referenzgebiete (blaue Polygone) innerhalb der 16 Teilkompartimenten (schwarze Polygone). In Hellgrün der günstige Luchshabitat, definiert durch ein Habitatmodell (Zimmermann 2004, Zimmermann & Breitenmoser 2007). Der Referenzgebiete (",Text.table[1,Refarea+1],") sowie der Teilkompartimenten (",names(Text.table)[Refarea+1],"), in dem diese Monitoring stattfand, sind hervorgehoben.](Plot_Einführung_Unterbereich.jpeg) 

\n",sep="")

```

\newpage

```{r Mat & Met FR,echo=FALSE,results='asis',eval=Language=="FR"}
cat("### Matériel et Méthode \n")

cat("Au total,",Sites," sites choisis avec l’aide des surveillants de la faune, les chasseurs et les naturalistes ont été échantillonés durant 60 nuits du ",paste(lubridate::day(Start),lubridate::month(Start),lubridate::year(Start),sep=".")," au ", paste(lubridate::day(Stop),lubridate::month(Stop),lubridate::year(Stop),sep=".")," à l'aide de ",Sites*2," pièges-photos (2 par sites) placés principalement le long de chemins forestiers et pédestres. Si un site a été déplacé lors de la session, l'ancien site ainsi que le nouveau sont pris en compte.",Text.table[6,names(Text.table)[Refarea+1]],"L’aire de référence présente une superficie de ", round(Refareashp$AREA_1[Refarea]/1000000,0)," km^2^, dont ", favorable," km^2^ d'habitat favorable au lynx (Zimmermann 2004; Zimmermann & Breitenmoser 2007)(Fig.2). L’unité de la taille de la population correspond au nombre de lynx âgés de plus d’un an (lynx indépendants), c’est-à-dire les lynx adultes résidents et les lynx subadultes qui se dispersent. Les lynx juvéniles sont aussi identifiés, mais ne sont pas pris en compte dans l’estimation d’abondance et de densité à cause de leur faible taux de détection et de leur fort taux de disparition (mortalité et dispersion). ")

if(JuvasMother==TRUE){
  cat("**Ils sont toutefois comptabilisés comme une capture de leur mère respective dans l'historique de capture.** 
      
      \n")
}

if(JuvasMother==FALSE){
  cat("**Dans cette session, ils ne sont pas comptabilisés comme une capture de leur mère.** 
      
      \n")
}

cat("![**Fig. 2.** Répartitions des sites (disques blancs) dans l'aire de référence ",Text.table[7,names(Text.table)[Refarea+1]]," (polygone bleu) au sein du sous-compartiment de gestion ",names(Text.table)[Refarea+1]," (polygone noir). En vert clair l’habitat favorable du lynx défini par un modèle d’habitat (Zimmermann 2004, Zimmermann & Breitenmoser 2007.](Plot_Introduction.jpeg)")


```

```{r Mat & Met DE,echo=FALSE,results='asis',eval=Language=="DE"}
cat("### Material und Methode \n")

cat("Insgesamt wurden",Sites," mit Hilfe von Wildbhüttern, Jägern und Naturschützern ausgewählte Standorte in 60 Nächten von ",paste(lubridate::day(Start),lubridate::month(Start),lubridate::year(Start),sep=".")," bis ",paste(lubridate::day(Stop),lubridate::month(Stop),lubridate::year(Stop),sep=".")," beprobt unter Verwendung von ",Sites*2," Fotofallen (2 pro Standort), die hauptsächlich entlang von Wald- und Wanderwegen aufgestellt wurden.Wenn ein Standort während der Session gewechselt wurde, werden sowohl der alte als auch der neue Standort berücksichtigt.",Text.table[5,names(Text.table)[Refarea+1]], "Das Referenzgebiet hat eine Fläche von ",round(Refareashp$AREA_1[Refarea]/1000000,0)," km^2^, von denen ",favorable," km^2^ luchsfreundlicher Lebensraum ist (Zimmermann 2004; Zimmermann & Breitenmoser 2007)(Abb.2). Die Einheit der Populationsgröße ist die Anzahl der Luchse, die älter als ein Jahr sind (unabhängige Luchse), d. h. ansässige erwachsene Luchse und umherstreifende subadulte Luchse. Jungluchse werden ebenfalls identifiziert, aber aufgrund ihrer geringen Entdeckungsrate und ihrer hohen Verschwindungsrate (Mortalität und Ausbreitung) nicht in die Schätzungen der Abundanz und Dichte einbezogen. ")


if(JuvasMother==TRUE){
  cat("**Sie werden jedoch in der Fanghistorie als Fang der jeweiligen Mutter gezählt.** 
      
      \n")
}

if(JuvasMother==FALSE){
  cat("**In dieser Monitoring werden sie nicht als Entführung von ihrer Mutter gezählt.** 
      
      \n")
}

cat("![**Abb. 2.** Verteilung der Standorte (weiße Scheiben) im Referenzgebiete ",Text.table[1,names(Text.table)[Refarea+1]]," (blaue Polygone) innerhalb der Teilkompartiment ",names(Text.table)[Refarea+1]," (schwarze Polygone). In Hellgrün der günstige Luchshabitat, definiert durch ein Habitatmodell (Zimmermann 2004, Zimmermann & Breitenmoser 2007).](Plot_Introduction.jpeg)")

```


\newpage

```{r Results Main FR,echo=FALSE,results='asis',eval=Language=="FR"}
cat("### Résultats et Discussion \n")

cat("La durée d’échantillonnage potentielle était de ",prettyNum(potentially.TN, big.mark="'")," nuits de captures. **Le vandalisme, des problèmes techniques, des erreurs de manipulation et la météo** ont ramené l’effort d’échantillonnage à ", prettyNum(effective.TN, big.mark="'")," nuits-pièges effectives, soit ", prettyNum(sprintf("%.1f",round((effective.TN*100)/potentially.TN,1)),decimal.mark = ",") ,"% du potentiel. **Cette valeur est raisonnable et se trouve dans la fourchette des valeurs qui ont été observées lors des autres monitorings menés par le KORA. Les sites positifs sont répartis de façon uniforme sur l'ensemble de la zone d'étude (Fig. 3) (Describe repartition).** 
    
\n")


cat("![**Fig. 3.** Distribution spatiale des lynx (Polygone Convexe Minimum + zone tampon) photographiès durant l'ensemble de la session déterministe. Bleu",paste("\ "),": mâle (zone tampon de 1,4 km), rose\ : femelle (1,2 km), noir\ : sexe inconnu (1 km). Disques blancs avec un point noir\ : sites où au moins une photo de lynx a été prise; **disques blancs avec un point rouge\ : sites où au moins une photo de lynx a été prise, mais l'individu n'a pas pu être identifié avec certitude; disques blancs avec un point vert\ : sites où au moins une photo de lynx a été prise, mais l'individu était un juvénile**; disques blancs\ : pas de photo de lynx. L'aire de référence est délimitée par le polygone bleu.](Map_Report.jpeg)",sep="")


```

```{r Results Main DE,echo=FALSE,results='asis',eval=Language=="DE"}
cat("### Resultate und Diskussion \n")

cat("Die potenzielle Probenahmezeit war ",prettyNum(potentially.TN, big.mark="'")," catch nights. **Vandalismus, technische Probleme, Bedienungsfehler und Wetter** reduzierten den Probenahmeaufwand auf ",prettyNum(effective.TN, big.mark="'")," tatsächliche Fallennächte, was ",prettyNum(sprintf("%.1f",round((effective.TN*100)/potentially.TN,1)),decimal.mark = ","),"% des Potenzials. **Dieser Wert ist angemessen und liegt im Bereich der Werte, die bei anderen KORA-Überwachungen beobachtet wurden. Die positiven Standorte sind gleichmäßig über das gesamte Untersuchungsgebiet verteilt (Abb. 3) (Beschreibung der Verteilung).** 

\n")

cat("![**Abb. 3.** Räumliche Verteilung von Luchsen (Minimum Convex Polygon + Pufferzone). Blau: Männchen (1,4 km Pufferzone), rosa: Weibchen (1,2 km), schwarz: unbekanntes Geschlecht (1 km). Weiße Scheiben mit einem schwarzem Punkt: Orte, an denen mindestens ein Foto eines Luchses gemacht wurde; weiße Scheiben mit einem rotem Punkt: Orte, an denen mindestens ein Foto eines Luchses gemacht wurde, das Individuum aber nicht mit Sicherheit identifiziert werden konnte; **weiße Scheiben mit einem grünem Punkt: Orte, an denen mindestens ein Foto eines Luchses gemacht wurde, das Individuum aber ein Jungtier war**; weiße Scheiben: kein Foto eines Luchses. Das Referenzgebiet ist durch eine grüne Polygon abgegrenzt.](Map_Report.jpeg)")

```

\newpage

```{r Call Lynx Table, echo=FALSE}
Event.report
```

\newpage

```{r Results Part 2 FR,echo=FALSE,results='asis',eval=Language=="FR"}
cat("#### Nombre minimum de lynx \n")

cat("**En tout, ", N.ind.lynx," lynx indépendants et ", N.juv," juvéniles de ", length(unique(Lynx.Table[Lynx.Table$YOB==juv.year & Lynx.Table$mother!="",mother]))," portées ont été détectés (voir Tab. 1)**. Ces lynx ont été photographiés sur", as.numeric(Event[ID=="Total",4])," des ",Sites," sites (", prettyNum(as.numeric(round((Event[ID=="Total",4]*100)/Sites,1)),decimal.mark = ",") ,"%) échantillonnés dans le cadre du monitoring. ",sep="")

if(length(Not.seen$ID)>0){
cat("Lors de cette session,",
length(Not.seen$ID),
" lynx ",
as.character(paste('(',paste(Not.seen$ID,collapse = ', '),')',sep='')),
"ont été observés dans le cadre du monitoring opportuniste sans avoir été photographié dans le cadre du monitoring déterministe.

\n")
}else{cat("

\n")}

cat("Un total de ",Event[ID=="Total",Event]," évènements ont été répertoriés au cours de la période d’échantillonnage de 60 nuits dans l’ensemble de l’aire de référence (Tab. 1). Ceux-ci ont été ramenées à",
ifelse(Period.selected==3,Occ.table.plot.3[20,SUM.occasion.cumulative], Occ.table.plot.5[12,SUM.occasion.cumulative])
," par le groupement des détections par occasion (est égale à", ifelse(Period.selected==3,3,5) ,"nuits consécutives lors de cette étude). Si un lynx est photographié à plusieurs reprises pendant une même occasion, il compte comme une seule capture. **Vu que le nombre de captures cumulées augmente constamment, nous pouvons raisonnablement conclure que les lynx n'ont pas commencés à éviter les sites au cours de la période d'échantillonage (Fig. 4). De plus une grande partie des lynx présents dans l’aire de référence ont dû être détectés vu que le nombre de lynx capturés se stabilise déjà à partir de la XXXXième occasion.** \n")



if(length(Seen.external)==0){
cat("**Lors de cette session, il n’y a pas eu de lynx qui ont été détectés en dehors de la période d’étude. Tous les lynx détectés ont donc été comptabilisés dans le calendrier de capture en vue des analyses de capture-recapture.** 

\n")
}else{
cat("**Lors de cette session, le(s) lynx ", paste(Seen.external, collapse = ", "),"a/ont uniquement été détecté(s) en dehors de la période d’étude. Ce(s) lynx apparaisse(nt) sur la carte (Fig. 3.) mais ne sont pas pris en compte dans le reste des analyses. Ce(s) lynx est/sont pris en compte dans l'incertitude du model.** 
    
\n") 
  
}

cat("![**Fig. 4.** Evolution du nombre de captures de lynx cumulées et du nombre de lynx capturés dans l'aire de référence",Text.table[7,Refarea+1],". Si un lynx est photographié à plusieurs reprises pendant une même occasion, il compte comme une seule capture.  
\n](Plot_cumulative_report.jpeg)")

```

```{r Results Part 2 DE,echo=FALSE,results='asis',eval=Language=="DE"}
cat("#### Minimale  Anzahl  Luchse \n")

cat("**Insgesamt wurden ", N.ind.lynx," unabhängige Luchse und ", N.juv," Jungtiere von ", length(unique(Lynx.Table[Lynx.Table$YOB==juv.year & Lynx.Table$mother!="",mother]))," Würfen festgestellt (siehe Tab. 1)**. Diese Luchse wurden an", as.numeric(Event[ID=="Gesamt",4])," Standorten ",Sites," (", prettyNum(as.numeric(round((Event[ID=="Total",4]*100)/Sites,1)),decimal.mark = ","),"%) fotografiert, die im Rahmen des Monitorings eingerichtet wurden. ",sep="")

if(length(Not.seen$ID)>0){
cat("Bei dieser Session wurden",
length(Not.seen$ID),
" Luchse ",
as.character(paste('(',paste(Not.seen$ID,collapse = ', '),')',sep='')),
"im Rahmen des opportunistischen Monitorings beobachtet, ohne dass sie im Rahmen des deterministischen Monitorings fotografiert worden waren.

\n")
}else{cat("

\n")}

cat("Insgesamt wurden während des Probenahmezeitraums im gesamten Bezugsgebiet ",Event[ID=="Insgesamt",Event]," Ereignisse aufgezeichnet (Tab. 1). Diese wurden reduziert auf",ifelse(Period.selected==3,Occ.table.plot.3[20,SUM.occasion.cumulative], Occ.table.plot.5[12,SUM.occasion.cumulative]),"
durch Gruppierung der Entdeckungen nach Anlass (in dieser Studie Zeitraum von", ifelse(Period.selected==3,3,5) , "aufeinanderfolgenden Nächten). Wird ein Luchs mehrmals bei der gleichen Gelegenheit fotografiert, zählt dies als ein Fang. **Die Zahl der kumulativen Erfassungen nimmt ständig zu (Abb. 4). Der kontinuierliche Anstieg der kumulierten Erfassungen ist ein Indiz für einen erfolgreichen Durchgang. Da es keinen andauernden grossflächigen Einbruch in der Funktionalität der Fotofallen gab, können wir daraus schliessen, dass Luchse keine Scheu vor den Fotofallen entwickelten.
** \n")


if(length(Seen.external)==0){
cat("**Während dieser Monitoring wurden keine Luchse außerhalb des Untersuchungszeitraums entdeckt. Alle entdeckten Luchse wurden daher in den Fangplan für die Fang-Wiederfang-Analysen aufgenommen.**
    
\n")
}else{
cat("**Während dieser Sitzung wurde(n) der/die Luchs(e) ", paste(Seen.external, collapse = ", "), "nur außerhalb des Untersuchungszeitraums entdeckt. Diese Luchse erscheinen auf der Karte (Abb. 3), werden aber in den übrigen Analysen nicht berücksichtigt. Diese(r) Luchs(e) werden bei der Modellunsicherheit berücksichtigt.**
    
\n") 
  
}

cat("![**Abb. 4.** Entwicklung der Anzahl der gefangenen Luchse und der Anzahl der im Referenzgebiet ",Text.table[1,Refarea+1]," gefangenen Luchse. Wird ein Luchs mehr als einmal bei der gleichen Gelegenheit fotografiert, zählt dies als ein Fang.**  

\n](Plot_cumulative_report.jpeg)")

```

\newpage

```{r Results Part 3 FR,echo=FALSE,results='asis', eval=Language=="FR"}

cat("#### Estimation de l'abondance et de la densité \n")


#Description du modèle:
model.descritption<-data.table(Model=c("0","b","h","t"),
                               Description=c("**qui considère que la probabilité de capture est constante**", #M0
                      "**qui considère que la probabilité de capture varie du à une réponse biologique**", #Mb
                      "**qui considère que la probabilité de capture varie d'un individu à l'autre mais ne varie pas au cours du temps**", #Mh
                      "**qui considère que la probabilité de capture varie en fonction du temps**")) #Mt

model.descritption<-model.descritption[model.descritption$Model==substr(Mark.Table.inline[which.best.model.selected,Model], 2, 2),Description]


cat("Sous le modèle ",paste("M~",substr(Mark.Table.inline[which.best.model.selected,Model], 2, 2),"~",sep=""),", ",model.descritption,", l’estimation de l’abondance (intervalle de confiance de 95%) par capture-recapture était de ",
paste(Mark.Table.inline[which.best.model.selected,N]," (",gsub("[.]",",",sprintf("%.0f",round(Mark.Table.inline[which.best.model.selected,"N"]-1.96*Mark.Table.inline[which.best.model.selected,"SE"],0))),"-",gsub("[.]",",",sprintf("%.0f",round(Mark.Table.inline[which.best.model.selected,"N"]+1.96*Mark.Table.inline[which.best.model.selected,"SE"],0))),sep=""),") lynx indépendants. Ainsi, ", prettyNum(as.numeric(sprintf("%.1f",round((length(Lynx.Table.Adult$ID)*100)/Mark.Table.inline[which.best.model.selected,N],1))),decimal.mark = ","),"% des lynx estimés ont effectivement été photographiés. 
\n",sep="")


```

```{r Results Part 3 DE,echo=FALSE,results='asis', eval=Language=="DE"}

cat("#### Schätzung der Abundanz und Dichte \n")

#Description du modèle:
model.descritption<-data.table(Model=c("0","b","h","t"),
                               Description=c("**bei dem davon ausgegangen wird, dass die Wahrscheinlichkeit des Fangens konstant ist**", #M0
                      "**bei dem davon ausgegangen wird, dass die Fangwahrscheinlichkeit aufgrund einer biologischen Reaktion variiert**", #Mb
                      "**bei dem davon ausgegangen wird, dass die Wahrscheinlichkeit, gefasst zu werden, von einem Individuum zum anderen variiert, aber nicht im Laufe der Zeit schwankt**", #Mh
                      "**bei dem davon ausgegangen wird, dass die Wahrscheinlichkeit des Fangens mit der Zeit variiert**")) #Mt

model.descritption<-model.descritption[model.descritption$Model==substr(Mark.Table.inline[which.best.model.selected,Model], 2, 2),Description]


cat("Unter dem Modell ",paste("M~",substr(Mark.Table.inline[which.best.model.selected,Model], 2, 2),"~",sep=""),", ",model.descritption,", die Schätzung der Abundanz (95% Konfidenzintervall) durch Fang-Wiederfang war ",
paste(Mark.Table.inline[which.best.model.selected,N]," (",gsub("[.]",",",sprintf("%.0f",round(Mark.Table.inline[which.best.model.selected,"N"]-1.96*Mark.Table.inline[which.best.model.selected,"SE"],0))),"-",gsub("[.]",",",sprintf("%.0f",round(Mark.Table.inline[which.best.model.selected,"N"]+1.96*Mark.Table.inline[which.best.model.selected,"SE"],0))),sep=""),")  selbständigen  Luchsen, ", prettyNum(as.numeric(sprintf("%.1f",round((length(Lynx.Table.Adult$ID)*100)/Mark.Table.inline[which.best.model.selected,N],1))),decimal.mark = ","),"% der geschätzten Luchse wurden tatsächlich fotografiert. 
\n", sep="")


```

```{r Results Part 4 FR,echo=FALSE,results='asis', eval=Language=="FR"}
cat("La densité (intervalle de confiance de 95%) dans l’aire de référence était de ",
    Density.surface," (",Density.surface.min95,"-",Density.surface.max95,") lynx indépendants pour 100 km^2^ ou ",
      Density.surface.favorable," (",Density.surface.favorable.min95,"-",Density.surface.favorable.max95,") lynx indépendants pour 100 km^2^ d’habitat favorable (Fig.5). 
    
\n")


cat("![**Fig. 5.** Evolution des densités de lynx indépendants pour 100 km^2^ d’habitat favorable dans l’aire de référence (histogramme avec intervalle de confiance de 95%) du ",Text.table[7,Refarea+1],".

\n](History_denisty_plot.jpeg)",sep="")
```

```{r Results Part 4 DE,echo=FALSE,results='asis', eval=Language=="DE"}
cat("Die Dichte (95% Konfidenzintervall) im Referenzgebiet betrug ",
    Density.surface," (",Density.surface.min95,"-",Density.surface.max95,") selbständiger Luchse pro 100 km^2^ oder ",
      Density.surface.favorable," (",Density.surface.favorable.min95,"-",Density.surface.favorable.max95,") selbständiger Luchse pro 100 km^2^  geeignetem Habitat (Abb.5). 
    
\n")

cat("![**Abb. 5.** Entwicklung der unabhängigen Luchsdichten pro 100 km^2^ günstigen Lebensraums im Referenzgebiet (Histogramm mit 95 % Konfidenzintervall) von ",Text.table[1,Refarea+1],".

\n](History_denisty_plot.jpeg)",sep="")

```

\newpage

```{r Results Part 5 FR,echo=FALSE,results='asis',eval=Language=="FR"}
cat("#### Comparaison avec les densités estimées dans les autres aires de référence 
    
\n")

cat("**La densité estimée pour 100 km^2^ d’habitat favorable dans le ",Text.table[7,Refarea+1]," (",
      paste(prettyNum(History[length(History$Year),Density],decimal.mark=",")," (",
      prettyNum(History[length(History$Year),Min95],decimal.mark=","),
      "-",
      prettyNum(History[length(History$Year),Max95],decimal.mark=","),")",sep=""),") ne diffère pas significativement des valeurs les plus récentes estimées dans les autres aires de référence à l’exception de celle mesurée dans l’Ouest de la Suisse centrale et le Haut-Valais (Tab. 2). Elle se situe parmi les plus hautes jamais estimées dans l’ensemble de la Suisse.**",sep="")

```

```{r Results Part 5 DE,echo=FALSE,results='asis',eval=Language=="DE"}
cat("#### Vergleich mit geschätzten Dichten in anderen Referenzgebieten 
    
\n")

cat("**Die geschätzte Dichte pro 100 km^2^ an geeignetem Lebensraum im ",Text.table[1,Refarea+1]," (",
      paste(prettyNum(History[length(History$Year),Density],decimal.mark=",")," (",
      prettyNum(History[length(History$Year),Min95],decimal.mark=","),
      "-",
      prettyNum(History[length(History$Year),Max95],decimal.mark=","),")",sep=""),") unterscheidet sich nicht signifikant von den zuletzt geschätzten Werten in den anderen Referenzgebieten, mit Ausnahme derjenigen, die in der westlichen Zentralschweiz und im Oberwallis gemessen wurde (Tab. 2). Sie gehört zu den höchsten, die je für die gesamte Schweiz geschätzt wurden.**",sep="")

```

```{r Call Density comparaison Table, echo= FALSE}
History.comparaison
```



\newpage

```{r Tail Report FR,echo=FALSE,results='asis',eval=Language=="FR"}
cat("### Remerciements \n")

cat("Nous remercions vivement tous ceux qui d’une manière ou d’une autre nous ont aidés et
soutenus. En particulier\ : 

\n")

cat("- tous les responsables des institutions cantonales et fédérales notamment", 
    paste(Text.table[2,names(Text.table)[Refarea+1]]),
    paste(Text.table[4,names(Text.table)[Refarea+1]]),"pour leur soutien professionnel.
    
    \n")

cat("- tous les surveillants de  la faune, surveillants auxiliaires de la  faune  et naturalistes qui nous ont  aidés lors du choix  des sites ainsi  que  lors  de  la mise  en place  des pièges-photos, les contrôles et le  démontage,  en particulier\ :", paste(gsub(",","",sort(unique(DataFULL[,site_controller])[!unique(DataFULL[,site_controller]) %in% "KORA"])),collapse=", "),";

\n")




cat("- tous les civilistes, stagiaires et collaborateurs au KORA qui ont participé au projet\ : **XXXXX**.

\n")

cat("### Références 

\n")

cat("Laass, J. 1999. *Evaluation von Photofallen für ein quantitatives Monitoring einer Luchspopulation in den Schweizer Alpen.*. Universität Wien, Wien. 

\n")

cat("R Core Team.  2021. *A Language and Environment for Statistical Computing*. R Foundation for Statistical
  Computing, Vienna, Austria. URL: https://www.R-project.org/. 

\n")

cat("Zimmermann,  F.  2004.  *Conservation  of  the  Eurasian  lynx  (Lynx  lynx) in  a  fragmented  landscape  –  habitat  models, dispersal,  and  potential distribution*.  PhD  Thesis,  Department  of  Ecology  and  Evolution,  University  of  Lausanne, Switzerland. 
    
\n")

cat("Zimmermann, F. & Breitenmoser, U. 2007. *Potential distribution and population size of the Eurasian lynx (Lynx lynx) in the Jura Mountains and possible corridors to adjacent ranges.* Wildlife Biology 13: 406–416. 
    
\n")

  
cat("**Citation proposée\ :** 
\n")

cat(paste(Authors,", ",data.table::year(Sys.time()),". ",Title," KORA Bericht xx, 12pp. 
\n",sep=""))


cat("**Géodonnées\ :** 
\n")
  
cat("Toutes les analyses et le traitement des données ont été effectués à l'aide du langage et de l'environnement de programmation statistique R 4.1.0 (R Core Team, 2021). Les données utilisées pour créer le fond de carte ont été extraites de l'Open Street Map (https://www.openstreetmap.org/). La Fig. 1 ainsi que les cartes en annexe contiennent la couche altitudinale et la couche des lacs de GEOSTAT, © Bundesamt für Statistik; Euromaps, © Bartholomew.
\n")


```


```{r Tail Report DE,echo=FALSE,results='asis',eval=Language=="DE"}
cat("### Danksagung \n")

cat("Wir danken allen ganz herzlich, die uns in irgendeiner Form unterstützt haben. Besonders danken wir: 
    
\n")

cat("- allen  Verantwortlichen der beteiligten kantonalen  und eidgenössischen  Institutionen, namentlich", 
    paste(Text.table[2,names(Text.table)[Refarea+1]]),
    paste(Text.table[3,names(Text.table)[Refarea+1]]),"für ihre  professionelle  Unterstützung.
    
    \n")

cat("- allen Wildhütern, freiwilligen Jagdaufsehern, Jägern und Naturfreunden, die  uns bei der Wahl der  Standorte,  sowie  bei den Kontrollen und  dem Abbruch der Fotofallen geholfen haben, insbesondere: ", paste(gsub(",","",sort(unique(DataFULL[,site_controller])[!unique(DataFULL[,site_controller]) %in% "KORA"])),collapse=", "),";

\n")

cat("- alle Zivi, Praktikanten und KORA-Mitarbeiter, die an dem Projekt teilgenommen haben: XXXXX (remove 'KORA' above).

\n")


cat("### Referenzen 
    
\n")

cat("Laass, J. 1999. *Evaluation von Photofallen für ein quantitatives Monitoring einer Luchspopulation in den Schweizer Alpen.*. Universität Wien, Wien. 

\n")

cat("R Core Team.  2021. *A Language and Environment for Statistical Computing*. R Foundation for Statistical
  Computing, Vienna, Austria. URL: https://www.R-project.org/. 

\n")

cat("Zimmermann,  F.  2004.  *Conservation  of  the  Eurasian  lynx  (Lynx  lynx) in  a  fragmented  landscape  –  habitat  models, dispersal,  and  potential distribution*.  PhD  Thesis,  Department  of  Ecology  and  Evolution,  University  of  Lausanne, Switzerland. 
    
\n")

cat("Zimmermann, F. & Breitenmoser, U. 2007. *Potential distribution and population size of the Eurasian lynx (Lynx lynx) in the Jura Mountains and possible corridors to adjacent ranges.* Wildlife Biology 13: 406–416. 
    
\n")
  
cat("**Vorgeschlagene Zitierung:** 
\n")

cat(paste(Authors,", ",data.table::year(Sys.time()),". ",Title," KORA Bericht xx, 12pp. \n",sep=""))


cat("**Digitale geografische Daten:** 
\n")
  
cat("Alle Datenanalysen und die Datenverarbeitung wurden mit der statistischen Programmiersprache und Umgebung R 4.1.0 (R Core Team, 2021) durchgeführt. Die Daten, die für die Erstellung des Kartenhintergrunds verwendet wurden, stammen aus der Open Street Map (https://www.openstreetmap.org/). Abb. 1 und die beigefügten Karten enthalten die Höhen- und Seenschicht von GEOSTAT, © Bundesamt für Statistik; Euromaps, © Bartholomew.
\n")

```


\newpage

```{r Appendix FR, echo=FALSE,results='asis',eval=Language=="FR"}
cat("### Annexe \n")
```

```{r Appendix DE, echo=FALSE,results='asis',eval=Language=="DE"}
cat("### Anhang \n")
```

```{r Opp Canis lupus FR,echo=FALSE, eval= Language=="FR" & "Canis lupus" %in% Species.other, fig.width = 16.5, fig.height= 20, fig.cap = "Fig. Annexe *Canis lupus*\ : distribution des sites positifs (points noirs) et des sites sans détections (disques blancs) dans l'aire de référence (polygone bleu) du sous-compartiment de gestion (polygon noir). Un site est considéré comme positif lorsqu'au moins un loup (*Canis lupus*) y a été photographié."}
Plot_KORA_Report("Canis lupus")
```

```{r Opp Canis lupus DE,echo=FALSE, eval= Language=="DE" & "Canis lupus" %in% Species.other, fig.width = 16.5, fig.height= 20, fig.cap = "Abb. Anhang *Canis lupus*: Verteilung der positiven Standorte (schwarze Punkte) und der Standorte ohne Nachweise (weiße Scheiben) im Referenzgebiet (blaues Polygon) des Teilgebiets Management (schwarzes Polygon). Ein Standort gilt als positiv, wenn mindestens ein Wolf (*Canis lupus*) dort fotografiert wurde."}
Plot_KORA_Report("Canis lupus")
```

```{r Opp Felis silvestris FR,echo=FALSE, eval= Language=="FR" & "Felis silvestris" %in% Species.other, fig.width = 16.5, fig.height= 20, fig.cap = "Fig. Annexe *Felis silvestris*\ : distribution des sites positifs (points noirs) et des sites sans détections (disques blancs) dans l'aire de référence (polygone bleu) du sous-compartiment de gestion (polygon noir). Un site est considéré comme positif lorsqu'au moins un chat sauvage (*Felis silvestris*) y a été photographié."}
Plot_KORA_Report("Felis silvestris")
```

```{r Opp Felis silvestris DE,echo=FALSE, eval= Language=="DE" & "Felis silvestris" %in% Species.other, fig.width = 16.5, fig.height= 20, fig.cap = "Abb. Anhang *Felis silvestris*: Verteilung der positiven Standorte (schwarze Punkte) und der Standorte ohne Nachweise (weiße Scheiben) im Referenzgebiet (blaues Polygon) des Teilgebiets Management (schwarzes Polygon). Ein Standort gilt als positiv, wenn mindestens ein Wildkatze (*Felis silvestris*) dort fotografiert wurde."}
Plot_KORA_Report("Felis silvestris")
```

```{r Opp Canis aureus FR,echo=FALSE, eval= Language=="FR" & "Canis aureus" %in% Species.other, fig.width = 16.5, fig.height= 20, fig.cap = "Fig. Annexe *Canis aureus*\ : distribution des sites positifs (points noirs) et des sites sans détections (disques blancs) dans l'aire de référence (polygone bleu) du sous-compartiment de gestion (polygon noir). Un site est considéré comme positif lorsqu'au moins un chacal doré (*Canis aureus*) y a été photographié."}
Plot_KORA_Report("Canis aureus")
```

```{r Opp Canis aureus DE,echo=FALSE, eval= Language=="DE" & "Canis aureus" %in% Species.other, fig.width = 16.5, fig.height= 20, fig.cap = "Abb. Anhang *Canis aureus*: Verteilung der positiven Standorte (schwarze Punkte) und der Standorte ohne Nachweise (weiße Scheiben) im Referenzgebiet (blaues Polygon) des Teilgebiets Management (schwarzes Polygon). Ein Standort gilt als positiv, wenn mindestens ein Goldschakal (*Canis aureus*) dort fotografiert wurde."}
Plot_KORA_Report("Canis aureus")
```

\newpage

##### KORA Appendix

###### This part can be removed from the report. It is produced for KORA people writing the report. When finishing the report, one should 1) check that all sites had at least one picture, 2) choose model and re-run the script, 3) check all sentences written in **bold**, 4) adapt the number of pages in the citation, 5) adapt the XX of the KORA Bericht xx, 6)For french reports, change the space before ":". Always consider the output as a first draft and not as a final version. Every session could present it's own exceptions chich will ask for an improvement/correction of the script. 

\n

\n

```{r Call Mark.Table, echo=FALSE}
Mark.Table
```

\n

\n

```{r Call table Opp. mon,echo=FALSE}

Opp.table

```

\newpage

![Fig. KORA.1 Cumulative number of occasion (black) and cummulative number of lynx ID (blue). Left = 20 occasions, right = 12 occasions. Closure test should be > 0.05 if the population is closed. The blue line should flatten itself. This shows that we captured most of the lynx ID in the area. The black line should grow constantly. This shows that lynx do not avoid camera traps after their first capture.](Plot_cumulative.jpeg)


\newpage


![Fig. KORA.2 The opportunistic monitoring represents here the opportunistic observations that took place during the monitoring period and that were transmitted to KORA. Only observations made in the study area are selected. The blue line delimits the study area. In colour: areas of lynx activity (Minimum Convex Polygon + 2 km buffer zone); black dots: sites were lynx were seen; orange dots: sightings of unidentifiable lynx (U).](Plot_Opp_Mon.jpeg)

\newpage

```{r Call Table.Dispersal,echo=FALSE}

Dispersal

```

\newpage

```{r Call Table.Sites. mon,echo=FALSE}

Table.Sites

```


